---
title: "01_univariate_Draft2_EDM.Rmd"
output: html_document
date: "2025-04-28"
editor_options: 
  chunk_output_type: console
  
  
---

#LIBRARY
```{r}

library(tidyverse)
library(googlesheets4)
library(oce)
library(padr)
library(rEDM)
library(ggplot2)
library(zoo)
library(quantreg)
library(dplyr)

```


#DATA SETS
```{r}

# ag_df_CR <- na.omit(ag_df_CR)
# morndf_CR
# df_CR

```


#DAILY TIME SERIES CLASSIFICATION

## ACF DAILY/WEEKLY

Conclusion:
PHY -> 6 - 11 days
CHL -> 3 -6 days

```{r}

ts_chl_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)

acf(ts_chl_2021,lag.max = 30, main = "Daily Chlorophyll (RFU) ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
acf(ts_phy_2021,lag.max = 30, main = "Daily Phycocanin  (RFU) ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))



```

## PACF DAILY/WEEKLY

```{r}
pacf2021 <- ag_df_CR %>% 
  filter(year(date)==2021) %>%
  pull(chl) %>%
  pacf(lag.max= 14)
plot(pacf2021, main = "Daily Chlorophyll (RFU) PACF")

pacf2021 <- ag_df_CR %>% 
  filter(year(date)==2021) %>%
  pull(phy) %>%
  pacf(lag.max= 14)
plot(pacf2021, main = "Daily Phyocanin (RFU) PACF")
```


# UNI EDM DAILY


## UNI 1 DAY

#### Data Config 1 DAY

```{r}

tau_i <- 1 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 1 DAY
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]

simplexE <- best_simplex_selectE_row$E
max_simplex_phy_tau1 <-best_simplex_selectE_row$rho

```

#### SMap - Select Theta No Ex 1 DAY

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta



```


#### SMap - Eval Exclusion Radius 1 DAY - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 1 DAY


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau1 <- print(smapstats$rho)

```


## UNI 2 DAYS

#### Data Config 2 DAYS

```{r}

tau_i <- 2 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 2 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E

max_simplex_phy_tau2 <-best_simplex_selectE_row$rho

```

#### SMap - Select Theta No Ex 2 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta

#RESULT: 



```


#### SMap - Eval Exclusion Radius 2 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 2 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau2 <- print(smapstats$rho)

```


## UNI 3 DAYS 

#### Data Config 3 DAYS

```{r}

tau_i <- 3 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 3 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E


max_simplex_phy_tau3 <-best_simplex_selectE_row$rho

```

#### SMap - Select Theta No Ex 3 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta




```


#### SMap - Eval Exclusion Radius 3 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 3 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau3 <- print(smapstats$rho)

```


## UNI 4 DAYS 

#### Data Config 4 DAYS

```{r}

tau_i <- 4 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 4 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



simplexE <- simplex_selectE[which.max(simplex_selectE$rho), ]  
simplexE <- best_simplex_selectE_row$E
max_simplex_phy_tau4 <-best_simplex_selectE_row$rho




```

#### SMap - Select Theta No Ex 4 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta



```


#### SMap - Eval Exclusion Radius 4 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 4 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau4 <- print(smapstats$rho)

```




## UNI 5 DAYS 

#### Data Config 5 DAYS

```{r}

tau_i <- 5 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 5 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E


max_simplex_phy_tau5 <-best_simplex_selectE_row$rho

```

#### SMap - Select Theta No Ex 5 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta




```


#### SMap - Eval Exclusion Radius 5 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 5 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau5 <- print(smapstats$rho)

```




## UNI 6 DAYS 

#### Data Config 6 DAYS

```{r}

tau_i <- 6 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 6 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E

max_simplex_phy_tau6 <-best_simplex_selectE_row$rho


```

#### SMap - Select Theta No Ex 6 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta




```


#### SMap - Eval Exclusion Radius 6 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 6 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau6 <- print(smapstats$rho)

```




## UNI 7 DAYS/WEEKLY PHY 

#### Data Config 7 DAYS

```{r}

tau_i <- 7 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred


```


#### Simplex - Find Optimal E 7 DAYS PHY 
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E


max_simplex_phy_tau7 <-best_simplex_selectE_row$rho

max_simplex_phy_tau7

```

#### SMap - Select Theta No Ex 7 DAYS PHY

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta

#RESULT: 



```


#### SMap - Eval Exclusion Radius 7 DAYS PHY - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

simplexE_ex <- print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])

simplexE_ex <- simplexE_ex$rho


#### Smap - Make Predictions 7 DAYS PHY


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau7 <- print(smapstats$rho)

```



## UNI 8 DAYS 

#### Data Config 8 DAYS

```{r}

tau_i <- 8 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 8 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 


best_simplex_selectE_row <- print(simplex_selectE[which.max(simplex_selectE$rho), ])


max_simplex_phy_tau8 <- best_simplex_selectE_row$rho

simplexE <- best_simplex_selectE_row$E



```

#### SMap - Select Theta No Ex 8 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta




```


#### SMap - Eval Exclusion Radius 8 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 8 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau8 <- print(smapstats$rho)

```



## UNI 9 DAYS 

#### Data Config 9 DAYS

```{r}

tau_i <- 9 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 9 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E

```

#### SMap - Select Theta No Ex 9 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta

#RESULT: 

max_simplex_phy_tau9 <- print(best_simplex_theta_row$rho)


```


#### SMap - Eval Exclusion Radius 9 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 9 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i, showPlot = TRUE)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau9 <- print(smapstats$rho)

```



## UNI 10 DAYS 

#### Data Config 10 DAYS

```{r}

tau_i <- 10 #Days out

library(rEDM)

#UniVariate

ag_df_CR <- na.omit(ag_df_CR)
ag_df_CR$date <- as.Date(ag_df_CR$date)


first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

lib_ins <- c(1,1198) # data up through end of 2022; this is the training set
lib_oos <- c(1199,1374) # Pred




```


#### Simplex - Find Optimal E 10 DAYS
```{r}

#SELECT E - SIMPLEX

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i, maxE = 20, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 



best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E

max_simplex_phy_tau10 <-best_simplex_selectE_row$rho


```

#### SMap - Select Theta No Ex 10 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta



```


#### SMap - Eval Exclusion Radius 10 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])


#### Smap - Make Predictions 10 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau10 <- print(smapstats$rho)

```




# Linear Regression DAILY

```{r}


#1 DAY

tau_i <- 1

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau1 <- print(rho_AR1$rho)

#2 DAYS

tau_i <- 2

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau2 <- print(rho_AR1$rho)

#3 DAYS

tau_i <- 3

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau3 <- print(rho_AR1$rho)


#4 DAYS

tau_i <- 4

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau4 <- print(rho_AR1$rho)


#5 DAYS

tau_i <- 5

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau5 <- print(rho_AR1$rho)


#6 DAYS

tau_i <- 6

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau6 <- print(rho_AR1$rho)


#7 DAYS

tau_i <- 7

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau7 <- print(rho_AR1$rho)


#8 DAYS

tau_i <- 8

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau8 <- print(rho_AR1$rho)


#9 DAYS

tau_i <- 9

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau9 <- print(rho_AR1$rho)


#10 DAYS

tau_i <- 10

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill

AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = TRUE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

max_ar1_phy_tau10 <- print(rho_AR1$rho)


```



# Univar Histogram DAYS



```{r}

library(tibble)
library(ggplot2)

# Create the data frame with the values
Univar_rho_df <- tibble(
  value = c(
    max_ar1_phy_tau1, max_simplex_phy_tau1, max_smap_phy_tau1,
    max_ar1_phy_tau2, max_simplex_phy_tau2, max_smap_phy_tau2,
    max_ar1_phy_tau3, max_simplex_phy_tau3, max_smap_phy_tau3,
    max_ar1_phy_tau4, max_simplex_phy_tau4, max_smap_phy_tau4,
    max_ar1_phy_tau5, max_simplex_phy_tau5, max_smap_phy_tau5,
    max_ar1_phy_tau6, max_simplex_phy_tau6, max_smap_phy_tau6,
    max_ar1_phy_tau7, max_simplex_phy_tau7, max_smap_phy_tau7,
    max_ar1_phy_tau8, max_simplex_phy_tau8, max_smap_phy_tau8,
    max_ar1_phy_tau9, max_simplex_phy_tau9, max_smap_phy_tau9,
    max_ar1_phy_tau10, max_simplex_phy_tau10, max_smap_phy_tau10
  )
)

# Create model names and types
model_names <- c(
  "1 Day Linear Regression (AR1)", "1 Day Simplex", "1 Day S-map",
  "2 Day Linear Regression (AR1)", "2 Day Simplex", "2 Day S-map",
  "3 Day Linear Regression (AR1)", "3 Day Simplex", "3 Day S-map",
  "4 Day Linear Regression (AR1)", "4 Day Simplex", "4 Day S-map",
  "5 Day Linear Regression (AR1)", "5 Day Simplex", "5 Day S-map",
  "6 Day Linear Regression (AR1)", "6 Day Simplex", "6 Day S-map",
  "7 Day Linear Regression (AR1)", "7 Day Simplex", "7 Day S-map",
  "8 Day Linear Regression (AR1)", "8 Day Simplex", "8 Day S-map",
  "9 Day Linear Regression (AR1)", "9 Day Simplex", "9 Day S-map",
  "10 Day Linear Regression (AR1)", "10 Day Simplex", "10 Day S-map"
)

model_type <- rep(c("Linear Regression", "Simplex", "S-map"), times = 10)

univar_daily_rho <- tibble(
  name = factor(model_names, levels = model_names),
  value = Univar_rho_df$value,
  model_type = factor(model_type, levels = c("Linear Regression", "Simplex", "S-map"))
)

# Find the position before "6 Day Linear Regression (AR1)"
vline_position <- which(levels(univar_daily_rho$name) == "6 Day Linear Regression (AR1)") - 0.5

# Now plot
ggplot(univar_daily_rho, aes(x = name, y = value, fill = model_type)) +
  geom_col() +
  geom_vline(aes(xintercept = vline_position, color = "ACF Peak Complexity Zone"), 
             linetype = "dashed", size = 1.2, show.legend = TRUE) +
  scale_fill_manual(values = c("Linear Regression" = "red", 
                               "Simplex" = "green", 
                               "S-map" = "darkgreen")) +
  scale_color_manual(name = "", values = c("ACF Peak Complexity Zone" = "red")) +
  theme_minimal() +
  labs(x = "Model", y = "Prediction Skill (Ï)", title = "Phycocanin (RFU) Univariate Model Comparison", fill = "Model Type") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position = "top"
  )


```


#HOURLY TIME SERIES CLASSIFICATION

## ACF HOURLY


```{r}

ts_chl_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)

acf(ts_chl_2021,lag.max = 30, main = "Daily Chlorophyll (RFU) ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
acf(ts_phy_2021,lag.max = 30, main = "Daily Phycocanin  (RFU) ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))



```

## PACF HOURLY

```{r}
pacf2021 <- ag_df_CR %>% 
  filter(year(date)==2021) %>%
  pull(chl) %>%
  pacf(lag.max= 14)
plot(pacf2021, main = "Daily Chlorophyll (RFU) PACF")

pacf2021 <- ag_df_CR %>% 
  filter(year(date)==2021) %>%
  pull(phy) %>%
  pacf(lag.max= 14)
plot(pacf2021, main = "Daily Phyocanin (RFU) PACF")
```

### HOURLY UNI 

#MORN TIME SERIES CLASSIFICATION

## ACF MORN


```{r}

ts_chl_2021 <- morndf_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- morndf_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)

acf(ts_chl_2021,lag.max = 30, main = "Daily Chlorophyll (RFU) ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
acf(ts_phy_2021,lag.max = 30, main = "Daily Phycocanin  (RFU) ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))



```

## PACF MORN

```{r}
pacf2021 <- morndf_CR %>% 
  filter(year(date)==2021) %>%
  pull(chl) %>%
  pacf(lag.max= 14)
plot(pacf2021, main = "Daily Chlorophyll (RFU) PACF")

pacf2021 <- morndf_CR %>% 
  filter(year(date)==2021) %>%
  pull(phy) %>%
  pacf(lag.max= 14)
plot(pacf2021, main = "Daily Phyocanin (RFU) PACF")




```

### MORN UNI 



#UNIVAR HIST ALL DF


#PLOT SIMPLEX V. AR1


### AR1

```{r}
#7 DAYS PHY

lib_ins <- c(1,1198) 
lib_oos <- c(1199,1374) # Pred
columns_i <- "phy"
target_i <- "phy"
tau_i <- 7

AR1 <- SMap(dataFrame = ag_df_CR, columns = columns_i, target = target_i,
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = FALSE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

phy_max_ar1_phy_tau7 <- print(rho_AR1$rho)

#7 DAYS CHL

columns_i <- "chl"
target_i <- "chl"


AR1 <- SMap(dataFrame = ag_df_CR, columns = columns_i, target = target_i,
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = FALSE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

chl_max_ar1_phy_tau7 <- print(rho_AR1$rho)

#9:12 PHY

lib_ins <- c(1,1198)#CHANGE
lib_oos <- c(1199,1374) # CHANGE
columns_i <- "phy"
target_i <- "phy"
tau_i <- 24  #168 Hours in 7 days / 3 hours (9-12)

AR1 <- SMap(dataFrame = ag_df_CR, columns = columns_i, target = target_i,
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = FALSE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

mornphy_max_ar1_phy_tau24 <- print(rho_AR1$rho)

#9:12 CHL

lib_ins <- c(1,1198)#CHANGE
lib_oos <- c(1199,1374) # CHANGE
columns_i <- "chl"
target_i <- "chl"
tau_i <- 24  #168 Hours in 7 days / 3 hours (9-12) per day

AR1 <- SMap(dataFrame = ag_df_CR, columns = columns_i, target = target_i,
lib = lib_ins, pred = lib_oos, E=1,theta=0,tau=-tau_i,Tp=tau_i, showPlot = FALSE) #lib train, #pred is pred 

rho_AR1 <- ComputeError(AR1$predictions$Observations,
                        AR1$predictions$Predictions)

mornphy_max_ar1_phy_tau24 <- print(rho_AR1$rho)


```

## UNI 7 DAYS/WEEKLY SIMPLEX

```{r}


#DAILY PHY SIMPLEX 

library(rEDM)

df <- ag_df_CR #dataframe
lib_ins <- c(1,1198) 
lib_oos <- c(1199,1374) 

columns_i <- "phy"
target_i <- "phy"
tau_i <- 7 #Days out
E <- 25


#SIMPLEX 

simplex_selectE <- EmbedDimension(dataFrame = df, columns = columns_i, target = target_i,
 tau=-tau_i,Tp=tau_i, maxE = E, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 


best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E


#SMAP 

simplex_pred <- PredictNonlinear(dataFrame = df, columns = columns_i, target = columns_i,
 E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])

simplextheta <- best_simplex_theta_row$Theta


#MAX SIMPLEX
max_simplex_phy_tau7 <- best_simplex_selectE_row$rho 

#SIMPLEX VALUES
simplex_phy_tau7 <- simplex_selectE

#MAX SMAP
max_smap_phy_tau7 <- best_simplex_theta_row$rho 
#SMAP VALUES
smap_phy_tau7 <- simplex_pred




#DAILY CHL SIMPLEX 

library(rEDM)

df <- ag_df_CR #dataframe
lib_ins <- c(1,1198) #CHANGE 
lib_oos <- c(1199,1374) #CHANGE



columns_i <- "chl"
target_i <- "chl"
E <- 25
tau_i <- 7 #Days out

#SIMPLEX 

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = columns_i, target = target_i,
 tau=-tau_i,Tp=tau_i, maxE = E, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 


best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E


#SMAP 

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = columns_i, target = columns_i,
 E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])

simplextheta <- best_simplex_theta_row$Theta


#MAX SIMPLEX
max_simplex_chl_tau7 <- best_simplex_selectE_row$rho 

#SIMPLEX VALUES
simplex_chl_tau7 <- simplex_selectE 

#MAX SMAP
max_smap_chl_tau7 <- best_simplex_theta_row$rho 
#SMAP VALUES
smap_chl_tau7 <- simplex_pred




# 9 AM - 12 PM PHY


df <- morndf_CR #dataframe
lib_ins <- c(1,1198) #CHANGE 
lib_oos <- c(1199,1374) #CHANGE


columns_i <- "phy"
target_i <- "phy"

tau_i <- 24 #Days out
E <- 25


#SIMPLEX 

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = columns_i, target = target_i,
 tau=-tau_i,Tp=tau_i, maxE = E, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 


best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E


#SMAP 

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = columns_i, target = columns_i,
 E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])

simplextheta <- best_simplex_theta_row$Theta


#MAX SIMPLEX
max_simplex_phy_morntau24 <- best_simplex_selectE_row$rho 

#SIMPLEX VALUES
simplex_phy_morntau24 <- simplex_selectE 

#MAX SMAP
max_smap_phy_morntau24 <- best_simplex_theta_row$rho 

#SMAP VALUES
smap_phy_morntau24 <- simplex_pred


# 9 AM - 12 PM CHL


df <- morndf_CR #dataframe
lib_ins <- c(1,1198) #CHANGE 
lib_oos <- c(1199,1374) #CHANGE

columns_i <- "chl"
target_i <- "chl"

tau_i <- 24 #Days out
E <- 25


#SIMPLEX 

simplex_selectE <- EmbedDimension(dataFrame = ag_df_CR, columns = columns_i, target = target_i,
 tau=-tau_i,Tp=tau_i, maxE = E, 
lib = lib_ins, pred = lib_oos, showPlot = TRUE) #lib train, #pred is pred 


best_simplex_selectE_row <- simplex_selectE[which.max(simplex_selectE$rho), ]
simplexE <- best_simplex_selectE_row$E


#SMAP 

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = columns_i, target = columns_i,
 E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])

simplextheta <- best_simplex_theta_row$Theta


#MAX SIMPLEX
max_simplex_chl_morntau24 <- best_simplex_selectE_row$rho 

#SIMPLEX VALUES
simplex_chl_morntau24 <- simplex_selectE 

#MAX SMAP
max_smap_chl_morntau24 <- best_simplex_theta_row$rho 
#SMAP VALUES
smap_chl_morntau24 <- simplex_pred


```



```{r}


#MAX SIMPLEX

max_simplex_phy_tau7 

max_simplex_chl_tau7 

max_simplex_phy_morntau24 

max_simplex_chl_morntau24

#SIMPLEX VALUES

simplex_phy_tau7  

simplex_chl_tau7  

simplex_phy_morntau24 

simplex_chl_morntau24 


#MAX SMAP
max_smap_phy_tau7

max_smap_chl_tau7  

max_smap_phy_morntau24

max_smap_chl_morntau24

#SMAP VALUES

smap_phy_tau7 

smap_chl_tau7

smap_phy_morntau24

smap_chl_morntau24






```

#### PLOT SIMPLEX V. AR1 7 DAYS
```{r}

x_lim <- range(smap_phy_tau7$Theta)
y_lim <- range(smap_phy_tau7$rho)
y_padding <- 0.05 * diff(y_lim)


# Plot with line and custom axes limits
plot(x = smap_phy_tau7$Theta, 
     y = smap_phy_tau7$rho,
     type = "l", col = "lightblue", lwd = 2,
     xlab = "Theta (localization parameter)", ylab = "Prediction Skill (Ï)",
     main = "S-map V. AR(1) at 7 days",
     xlim = c(min(x_lim), max(x_lim)),
     ylim = c(min(y_lim) - y_padding, max(y_lim) + y_padding))


lines( x = smap_chl_tau7$Theta, y = smap_chl_tau7$rho, col = "green" )
lines(x = smap_phy_morntau24$Theta,  y = smap_phy_morntau24$rho, col = "red"   )
lines(x = smap_chl_morntau24$E,   y = smap_chl_morntau24$rho, col = "orange" )


abline(h = phy_max_ar1_phy_tau7, col = "darkblue", lty = 2)
abline(h = chl_max_ar1_phy_tau7, col = "darkgreen", lty = 2)
abline(h = mornphy_max_ar1_phy_tau24, col = "darkred", lty = 2)
abline(h = mornchl_max_ar1_phy_tau24, col = "darkorange", lty = 2)

# Add legend
legend("bottomright", legend = 
         c(
  "Daily Phycocanin (RFU) S-Map Forecast", 
   "Daily Phycocanin (RFU) AR(1)", 
 "Daily Chlorophyll (RFU) S-Map Forecast",
  "Daily Chlorophyll (RFU) AR(1)",
  "9 AM - 12 PM Phycocanin (RFU) S-Map Forecast",
  "9 AM - 12 PM Phycocanin (RFU) AR(1)",
 "9 AM - 12 PM Chlorophyll (RFU) S-Map Forecast",
 "9 AM - 12 PM Chlorophyll (RFU) AR(1)"
 ),
       col = c("lightblue", "darkblue", "green", "darkgreen", "red", "orange", "darkorange"), lty = c(1,2,1,2,1,2,1,2)) 

```


#### PLOT SMAP V. AR1 7 DAYS


#### PLOT SMAP V. AR1 7 DAYS
```{r}

x_lim <- range(simplex_selectE$E)
y_lim <- range(c(simplex_selectE$rho, max_ar1_phy_tau7))
y_padding <- 0.05 * diff(y_lim)


# Plot with line and custom axes limits
plot(x = simplex_phy_tau7$E, 
     y = simplex_phy_tau7$rho,
     type = "l", col = "lightblue", lwd = 2,
     xlab = "Embedding Dimension (E)", ylab = "Prediction Skill (Ï)",
     main = "Simplex V. AR(1) at 7 days",
     xlim = c(min(x_lim), max(x_lim)),
     ylim = c(min(y_lim) - y_padding, max(y_lim) + y_padding))


lines( x = simplex_chl_tau7$E, y = simplex_chl_tau7$rho, col = "green" )
lines(x = max_simplex_phy_morntau24$E,
  y = max_simplex_phy_morntau24$rho, col = "red"   )
lines(x = max_simplex_chl_morntau24$E,
  y = max_simplex_chl_morntau24$rho, col = "orange" )


abline(h = phy_max_ar1_phy_tau7, col = "darkblue", lty = 2)
abline(h = chl_max_ar1_phy_tau7, col = "darkgreen", lty = 2)
abline(h = mornphy_max_ar1_phy_tau24, col = "darkred", lty = 2)
abline(h = mornchl_max_ar1_phy_tau24, col = "darkorange", lty = 2)

# Add legend
legend("bottomright", legend = 
         c(
  "Daily Phycocanin (RFU) Simplex Forecast", 
   "Daily Phycocanin (RFU) AR(1)", 
 "Daily Chlorophyll (RFU) Simplex Forecast",
  "Daily Chlorophyll (RFU) AR(1)",
  "9 AM - 12 PM Phycocanin (RFU) Simplex Forecast",
  "9 AM - 12 PM Phycocanin (RFU) AR(1)",
 "9 AM - 12 PM Chlorophyll (RFU) Simplex Forecast",
 "9 AM - 12 PM Chlorophyll (RFU) AR(1)"
 ),
       col = c("lightblue", "darkblue", "green", "darkgreen", "red", "orange", "darkorange"), lty = c(1,2,1,2,1,2,1,2)) 

```



#PLOT SMAP V. AR1



#### SMap - Select Theta No Ex 7 DAYS

```{r}

#SELECT THETA

#w/o exclusion radius

simplex_pred <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E= simplexE ,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_oos, showPlot = TRUE) 


best_simplex_theta_row <- print(simplex_pred[which.max(simplex_pred$rho), ])


simplextheta <- best_simplex_theta_row$Theta


```


#### SMap - Eval Exclusion Radius 7 DAYS - TO DO


HELPER FUNCTION #ADD # here


eval_ex_radius <- function(dataFrame, columns, target, E, tau_i, lib_ins, lib_oos) {
  
  # Create an empty list to store results
  results_list <- list()
  
  # Loop over exclusionRadius values from 1 to 10
  for (ex_radius in 1:10) { #choose ex values
    
    tryCatch({
      result <- PredictNonlinear(
        dataFrame = dataFrame,
        columns = columns,
        target = target,
        E = E,
        tau = -tau_i,  
        Tp = tau_i,
        exclusionRadius = ex_radius,
        lib = lib_ins,
        pred = lib_oos,
        showPlot = FALSE
      )
      
      # Add exclusionRadius info
      result$exclusionRadius <- ex_radius
      
      # Store result
      results_list[[ex_radius]] <- result
      
    }, error = function(e) {
      # If error happens, store NA and print warning
      message(sprintf("Error at exclusionRadius = %d: %s", ex_radius, e$message))
      results_list[[ex_radius]] <- NA
    })
    
  }
  
  # Remove any NA results
  results_list_clean <- results_list[!sapply(results_list, is.na)]
  
  # Combine into a single dataframe
  if (length(results_list_clean) > 0) {
    results_select_ex <- do.call(rbind, results_list_clean)
  } else {
    results_select_ex <- data.frame()
  }
  
  return(results_select_ex)
}

eval_ex_radius_results <- eval_ex_radius(
  dataFrame = ag_df_CR,
  columns = "phy",
  target = "phy",
  E = 5,
  tau_i = tau_i,
  lib_ins = lib_ins,
  lib_oos = lib_oos
)

simplexE_ex <- print(eval_ex_radius_results[which.max(eval_ex_radius_results$rho), ])

simplexE_ex <- simplexE_ex$rho


#### Smap - Make Predictions 7 DAYS


```{r}

#PREDICT - SMAP

smap_pred <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_oos, E=simplexE,theta= simplextheta, tau = -tau_i, Tp = tau_i)

 smap_results <- as.data.frame(smap_pred[["predictions"]])


smapstats <- ComputeError(
                          smap_results$Observations,
                       smap_results$Predictions)

#RESULT: 

max_smap_phy_tau7 <- print(smapstats$rho)

```


#### PLOT SIMPLEX V. AR1 7 DAYS

```{r}

# Determine zoomed out limits
x_lim <- range(simplex_pred$Theta)
y_lim <- range(c(simplex_pred$rho, max_ar1_phy_tau7))
y_padding <- 0.05 * diff(y_lim)  # add 5% padding to y-axis


#plot 
plot(x = simplex_pred$Theta, y = simplex_pred$rho,
     type = "l", col = "blue", lwd = 2,
     xlab = "Theta (localization parameter)", ylab = "Prediction Skill (Ï)",
     main = "S-Map V. AR(1) at 7 days, Embedding Dimension = 3",
     xlim = c(min(x_lim), max(x_lim)),
     ylim = c(min(y_lim) - y_padding, max(y_lim) + y_padding))
abline(h = max_ar1_phy_tau7, col = "red", lty = 2)
legend("bottomright", legend = c("S-Map Forecast", "AR(1)"),
       col = c("blue", "red"), lty = c(1, 2), lwd = c(2, 1))


```


