
---
title: "01_univariate_EDM"
output: html_document
date: "2024-04-03"
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---



# Library

```{r}
library(tidyverse)
library(googlesheets4)
library(oce)
library(padr)
library(rEDM)
library(ggplot2)
library(zoo)
library(quantreg)
library(dplyr)

```



#EDM UNIVARIATE

# EDM

## EDM Uni-variate Analysis

## EDM 9-12 PHY

```{r}

#Without NA Values

morndf_CR <- readRDS("morndf_CR.rds")

# Find the first row number for the first date in 2023
first_row_2023 <- which(format(morndf_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

# Find the last value 
last_value <- nrow(morndf_CR)

print(last_value)

```

```{r}
lib_ins <- c(1,1084) # data up through end of 2022; this is the training set
lib_oos <- c(1085,1258) # leave this alone until we're nearly done with the project

rho_E <- EmbedDimension(dataFrame = morndf_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = morndf_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(color="blue") +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1)
  
```

4-days:

```{r}
tau_i <- 4

# Same as before but using a larger tau and setting Tp = tau

rho_E_tau_i_0 <- EmbedDimension(dataFrame = morndf_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


rho_E_tau_i <- EmbedDimension(dataFrame = morndf_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i,
                        exclusionRadius = tau_i, # exclude 2*tau additional points in cross-val
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = morndf_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E_tau_i %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(aes(color="correct")) +
  geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1) +
  labs(title=paste0("Simplex with tau = ",tau_i))
  
```

###Predict Nonlinear

```{r}
rho_theta_tau_i <- PredictNonlinear(dataFrame = morndf_CR, columns = "phy", target = "phy",
                                    E=3,
                                    tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

preds_AR1 <- SMap(dataFrame = morndf_CR, columns = "del_phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR1 <- ComputeError(preds_AR1$predictions$Observations,
                         preds_AR1$predictions$Predictions)


rho_theta_tau_i %>%
  ggplot(aes(x=Theta,y=rho)) + 
  geom_line() +
  # geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  # ylim(0,0.5) +
  labs(title=paste0("Simplex with tau = ",tau_i))

```

## EDM 9-12 1st Diff PHY

```{r}

#Without NA Values

morndf_CR <- na.omit(morndf_CR) 


# Find the first row number for the first date in 2023
first_row_2023 <- which(format(morndf_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

# Find the last value 
last_value <- nrow(morndf_CR)

print(last_value)

```

```{r}

rho_E <- EmbedDimension(dataFrame = morndf_CR, columns = "del_phy", target = "del_phy",
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = morndf_CR, columns = "del_phy", target = "del_phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(color="blue") +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1)
  

#rho_E <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
#lib = "1 1075", pred = "1076 1223", showPlot = TRUE) #lib train, #pred is pred 

#lib = "1 100 101 200 301 400", - leaving one out

```

4-days:

```{r}
tau_i <- 4

# Same as before but using a larger tau and setting Tp = tau

rho_E_tau_i_0 <- EmbedDimension(dataFrame = morndf_CR, columns = "del_phy", target = "del_phy",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


rho_E_tau_i <- EmbedDimension(dataFrame = morndf_CR, columns = "del_phy", target = "del_phy",
                        tau=-tau_i,Tp=tau_i,
                        exclusionRadius = tau_i, # exclude 2*tau additional points in cross-val
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = morndf_CR, columns = "del_phy", target = "del_phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E_tau_i %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(aes(color="correct")) +
  geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1) +
  labs(title=paste0("Simplex with tau = ",tau_i))
  
```

###Predict Nonlinear

```{r}
rho_theta_tau_i <- PredictNonlinear(dataFrame = morndf_CR, columns = "del_phy", target = "del_phy",
                                    E=8,
                                    tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

preds_AR1 <- SMap(dataFrame = morndf_CR, columns = "del_phy", target = "del_phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR1 <- ComputeError(preds_AR1$predictions$Observations,
                         preds_AR1$predictions$Predictions)


rho_theta_tau_i %>%
  ggplot(aes(x=Theta,y=rho)) + 
  geom_line() +
  # geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  # ylim(0,0.5) +
  labs(title=paste0("Simplex with tau = ",tau_i))

```

## EDM 9-12 CHL

```{r}

#Without NA Values

morndf_CR <- na.omit(morndf_CR) 


# Find the first row number for the first date in 2023
first_row_2023 <- which(format(morndf_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

# Find the last value 
last_value <- nrow(morndf_CR)

print(last_value)

```

```{r}

rho_E <- EmbedDimension(dataFrame = morndf_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = morndf_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(color="blue") +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1)
  

#rho_E <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
#lib = "1 1075", pred = "1076 1223", showPlot = TRUE) #lib train, #pred is pred 

#lib = "1 100 101 200 301 400", - leaving one out

```

4-days:

```{r}
tau_i <- 4

# Same as before but using a larger tau and setting Tp = tau

rho_E_tau_i_0 <- EmbedDimension(dataFrame = morndf_CR, columns = "chl", target = "chl",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


rho_E_tau_i <- EmbedDimension(dataFrame = morndf_CR, columns = "chl", target = "chl",
                        tau=-tau_i,Tp=tau_i,
                        exclusionRadius = tau_i, # exclude 2*tau additional points in cross-val
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = morndf_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E_tau_i %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(aes(color="correct")) +
  geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1) +
  labs(title=paste0("Simplex with tau = ",tau_i))
  
```

###Predict Nonlinear

```{r}
rho_theta_tau_i <- PredictNonlinear(dataFrame = morndf_CR, columns = "chl", target = "chl",
                                    E=9,
                                    tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

preds_AR1 <- SMap(dataFrame = morndf_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR1 <- ComputeError(preds_AR1$predictions$Observations,
                         preds_AR1$predictions$Predictions)


rho_theta_tau_i %>%
  ggplot(aes(x=Theta,y=rho)) + 
  geom_line() +
  # geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  # ylim(0,0.5) +
  labs(title=paste0("Simplex with tau = ",tau_i))

```

## EDM Daily CHL

```{r}

#Without NA Values
ag_df_CR <- readRDS("ag_df_CR.rds")
ag_df_CR <- na.omit(ag_df_CR) 


# Find the first row number for the first date in 2023
first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

# Find the last value 
last_value <- nrow(ag_df_CR)

print(last_value)

```

### Optimal Embedding Dimension

-   rho_E

    -   E

    -   Rho

```{r}
lib_ins <- c(1,1014) # data up through end of 2022; this is the training set
lib_oos <- c(1025,1189) # leave this alone until we're nearly done with the project

rho_E <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = ag_df_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(color="blue") +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1)
  

#rho_E <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
#lib = "1 1075", pred = "1076 1223", showPlot = TRUE) #lib train, #pred is pred 

#lib = "1 100 101 200 301 400", - leaving one out

```

"At a daily time-scale, EDM predictions do not beat the strong
day-to-day autocorrelation in the signal." This is no surprise. Let's
look again with a larger tau, informed by the previous ACF analysis; we
saw a signal somewhere in the window of 4 days - 1 week.

4-days:

```{r}
tau_i <- 4

# Same as before but using a larger tau and setting Tp = tau

rho_E_tau_i_0 <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


rho_E_tau_i <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
                        tau=-tau_i,Tp=tau_i,
                        exclusionRadius = tau_i, # exclude 2*tau additional points in cross-val
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = ag_df_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E_tau_i %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(aes(color="correct")) +
  geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1) +
  labs(title=paste0("Simplex with tau = ",tau_i))
  
```

```{r}
rho_theta_tau_i <- PredictNonlinear(dataFrame = ag_df_CR, columns = "chl", target = "chl",
                                    E=5,
                                    tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

preds_AR1 <- SMap(dataFrame = ag_df_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR1 <- ComputeError(preds_AR1$predictions$Observations,
                         preds_AR1$predictions$Predictions)


rho_theta_tau_i %>%
  ggplot(aes(x=Theta,y=rho)) + 
  geom_line() +
  # geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  # ylim(0,0.5) +
  labs(title=paste0("Simplex with tau = ",tau_i))

```

1 week:

```{r}
tau_i <- 7

# Same as before but using a larger tau and setting Tp = tau

rho_E_tau_i_0 <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


rho_E_tau_i <- EmbedDimension(dataFrame = ag_df_CR, columns = "chl", target = "chl",
                        tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = ag_df_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E_tau_i %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(aes(color="correct")) +
  geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1) +
  labs(title=paste0("Simplex with tau = ",tau_i))
  
```

```{r}

rho_theta_tau_i <- PredictNonlinear(dataFrame = ag_df_CR, columns = "chl", target = "chl",
                                    E=5,
                                    tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

preds_AR1 <- SMap(dataFrame = ag_df_CR, columns = "chl", target = "chl",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR1 <- ComputeError(preds_AR1$predictions$Observations,
                         preds_AR1$predictions$Predictions)


rho_theta_tau_i %>%
  ggplot(aes(x=Theta,y=rho)) + 
  geom_line() +
  # geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,0.5) +
  labs(title=paste0("Simplex with tau = ",tau_i))

```

## EDM Daily PHY

```{r}

#Without NA Values

ag_df_CR <- na.omit(ag_df_CR) 


# Find the first row number for the first date in 2023
first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

# Find the last value 
last_value <- nrow(ag_df_CR)

print(last_value)

```

### Optimal Embedding Dimension

-   rho_E

    -   E

    -   Rho

```{r}

rho_E <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(color="blue") +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1)
  
```

"At a daily time-scale, EDM predictions do not beat the strong
day-to-day autocorrelation in the signal." This is no surprise. Let's
look again with a larger tau, informed by the previous ACF analysis; we
saw a signal somewhere in the window of 4 days - 1 week.

4-days:

```{r}
tau_i <- 4

# Same as before but using a larger tau and setting Tp = tau

rho_E_tau_i_0 <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


rho_E_tau_i <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i,
                        exclusionRadius = tau_i, # exclude 2*tau additional points in cross-val
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E_tau_i %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(aes(color="correct")) +
  geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1) +
  labs(title=paste0("Simplex with tau = ",tau_i))
  
```

**E = 6 here?**

```{r}
rho_theta_tau_i <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E=4,
                                    tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

preds_AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR1 <- ComputeError(preds_AR1$predictions$Observations,
                         preds_AR1$predictions$Predictions)


rho_theta_tau_i %>%
  ggplot(aes(x=Theta,y=rho)) + 
  geom_line() +
  # geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  # ylim(0,0.5) +
  labs(title=paste0("Simplex with tau = ",tau_i))

```

1 week:

```{r}
tau_i <- 7

# Same as before but using a larger tau and setting Tp = tau

rho_E_tau_i_0 <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


rho_E_tau_i <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)


rho_E_tau_i %>%
  ggplot(aes(x=E,y=rho)) + 
  geom_line(aes(color="correct")) +
  geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,1) +
  labs(title=paste0("Simplex with tau = ",tau_i))
  
```

```{r}

rho_theta_tau_i <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E=2,
                                    tau=-tau_i,Tp=tau_i,exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 

preds_AR1 <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR1 <- ComputeError(preds_AR1$predictions$Observations,
                         preds_AR1$predictions$Predictions)


rho_theta_tau_i %>%
  ggplot(aes(x=Theta,y=rho)) + 
  geom_line() +
  # geom_line(data=rho_E_tau_i_0,aes(color="wrong")) +
  geom_hline(aes(yintercept = stats_AR$rho),lty=2,color="black") +
  ylim(0,0.5) +
  labs(title=paste0("Simplex with tau = ",tau_i))

```



