
---
title: "03_multivariate_EDM"
output: html_document
date: "2024-04-03"
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---


# EDM Mulit-variate Analysis 

#Multi Smap

#Library
```{r}

library(rEDM)
library(tidyverse)

```

#Option 1: highlighting nonlinearity test in-sample 

1 week:

```{r}
#SMAP - No exclusion radius 

tau_i <- 7

lib_ins <- c(1,1014) # data up through end of 2022; this is the training set
lib_oos <- c(1025,1189) # leave this alone until we're nearly done with the project

rho_theta_tau_i <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E=3,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, #pred is pred 


```

```{r}

rho_theta_tau_i #1) univar S-map

#2) multi w/ all var

columns_i <- c( "chl" ,     "phy"   ,   "ph"   ,    "Celsius" , "spcond" ,  "do" ,      "turb"  ,   "Salinity" , "sin_season")

multivar <- PredictNonlinear(dataFrame = ag_df_CR, columns = columns_i , target = "phy",
                                    E=3,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE, embedded = TRUE) #lib train, #pred is pred 

 
    if(file.exists("Multi_E3_D5.rds")) {
  # Load the file if it exists
  multivar <- readRDS("multivar.rds")
} else {
  # Save to file
  saveRDS(multivar, "multivar.rds") }

    
    
    
    
#3) multiview


Multi_E2_D3    #.rds

Multi_E2_D5 <- Mutliview_E2D5
  
Multi_E3_D5 <- readRDS("Multiview_E3D5.rds")

  
    save(Multi_E2_D5, file = "Multi_E2_D5.rds")


plot(Mutliview_E2D5)

print(Mutliview_E2D5$View$rho)

#plot
plot(x = rho_theta_tau_i$Theta, y = rho_theta_tau_i$rho, type = "l",
     main = "Nonlinear Tests", xlab = "Theta", ylab = "Rho", col = "blue", ylim = c(0, 1))

lines(x = multivar$Theta, y = multivar$rho, col = "red")

abline(h = max(Multi_E2_D5$View$rho), col = "green", lty = 2)

legend("topright", 
       legend = c("Univariate S-map", "Multivariate S-map", "Multiview"),
       col = c("blue", "red", "green"), 
       lty = c(1, 1, 2))


```


```{r}

#out of sample time series of predicted vs observed 


#The WHO found that cyanobacterial cell concentrations above 20,000 cells per ml are associated with “short term adverse health outcomes.

#a chlorophyll concentration of less than 10 μg/L is expected to correspond to a low probability of adverse health effects




```


Next Steps

Convergent Cross Mapping All possible Covariates in one data frame as
different columns other variables all the endogenous bigoeochemical and
human drivers management driver and - rainfall and CSOs know now half
week to weekly time scale we see has signature until we have the
corrected values to keep the diff 9 to noon 4 days negative auto, use
linear s-map To make forecasts: predict 1st differences and add back
into data prediction for tomorrow is value for tomorrow + value for
today

list of measurments and list of weekly measurments look at Tahoe +
geneva

plot minutes vs. volume CSOs - rainfall causal associations? analysis:
same trend = synchornity not = one is low and flat is oneway causal\
number at end matters, consider as correlation coeff, rho ccm at max
library size

look at full matrix with nutrient time series later on

2 different data matrixes 1. time-scale 2. timespan

#Multiview


ccm uses y to predict x, if true, x can affect y ccm wraps (Simplex
target = x, columns = y)

multivariate Simplex ( Embedded = True, columns = c("x1, "x2)) set CCM
samples to 10 to see result

Here, we demonstrate this idea using the Multiview() function with the
3-species data used above. Multiview() operates by constructing all
possible embeddings of dimension E with lag up to E-1. These embeddings
are ranked by forecast skill (rho) over the lib portion of the data. The
individual forecasts for the top multiview embeddings are then averaged
together. If multiview is not specified it is set to sqrt(C) where C is
the number of E-dimensional combinations created from all data vectors.

View lists the various combinations of data embedding vectors used for
the forecasts along with their prediction statistics. Predictions
returns the final averaged multiview projections.

E is amounts of lags. univar time lags D is dimension of individual
multivariate models, number of vars we're taking at a time. axis to
embed. Additional Analysis fills in mechnaistically. Can set lib = pred
At least E of 2, after E \> 5 com sci problem



```{r}


#Mutltiview

#Omit NAs 

ag_df_CR <- na.omit(ag_df_CR)


# Find the first row number for the first date in 2023
first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

#Check class

ag_df_CR$date <- as.numeric(ag_df_CR$date)
library(rEDM)


#**E3 D5 IN SAMPLE**

# Check if the file exists
if(file.exists("Multi_E3_D5.rds")) {
  # Load the file if it exists
  Multi_E3_D5 <- readRDS("Mutli_E3D5.rds")
} else {
  # If the file does not exist, create Multi_E2_D3
  Multi_E3_D5 <- Multiview(dataFrame = ag_df_CR, lib = "1 1014", pred = "1 1014", E =3, D=5,
                            columns = "chl phy ph Celsius spcond do turb Salinity sin_season", target = "phy")
  # Save Multi_E2_D3 to file
  saveRDS(Multi_E3_D5, "Mutli_E2D5.rds")
}



#**E2 D3 IN SAMPLE**

Multi_E2_D3 <- "Multi_E2_D3.rds"
if(!file.exists("Multi_E2_D3.rds")){
 Multi_E2_D3 <- Multiview(dataFrame = ag_df_CR, lib = "1 1014", pred = "1 1014", E = 2, D=3,
                            columns = "chl phy ph Celsius spcond do turb Salinity sin_season", target = "phy")
    save(Multi_E2_D3, file = "Multi_E2_D3.rds")
} else{
  load(Multi_E2_D3)
}


#HEAD


head(Multi_E2_D3)
  
head(Multi_E3_D5)
  
  

```





#END




