---
title: "Graveyard"
output: html_document
date: "2025-04-11"
---

#FIGURES AND TABLES



#TABLE All.Logan

#TABLE All.CR_nutrients

#TABLE All.bacteria



#PLOT 2021 DRIVERS

####Visualize Salinity

```{r}
#Visualize Salinity 2021 

df_CR <- df_CR %>% pad()

df_CR %>%
  mutate(date = as.Date(date)) %>%
  group_by(date) %>%
  filter(date >= as.Date("2021-05-01") & date <= as.Date("2021-11-01"))  %>%
  ggplot(aes(x = date)) + 
  geom_path(aes(y = Salinity, color = "Salinity")) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  ggtitle("Salinity 2021") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Month", y = "Salinity (ppm)")

#Visualize Chl 2021 

df_CR %>%
  mutate(date = as.Date(date)) %>%
  group_by(date) %>%
  filter(date >= as.Date("2021-05-01") & date <= as.Date("2021-11-01"))  %>%
  ggplot(aes(x = date)) + 
  geom_path(aes(y = chl, color = "chl")) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  ggtitle("Chlorophyll 2021") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Month", y = "Chlorophyll (RFU)")
  

#Visualize Phy 2021 

df_CR %>%
  mutate(date = as.Date(date)) %>%
  group_by(date) %>%
  filter(date >= as.Date("2021-05-01") & date <= as.Date("2021-11-01"))  %>%
  ggplot(aes(x = date)) + 
  geom_path(aes(y = chl, color = "phy")) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  ggtitle("Phycocanin 2021") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Month", y = "Phycocanin (RFU)")


df_CR %>% group_by(date,hour) %>%
    mutate(date = as.Date(date)) %>%
  group_by(date) %>%
  filter(date >= as.Date("2021-05-01") & date <= as.Date("2021-11-01"))  %>%
  ggplot(aes(x=date)) + 
  geom_path(aes(y=chl,color="chl")) + 
  geom_path(aes(y=phy,color="phy")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle(" < 2021 Chlorophyll V. Phycocanin ") + 
    labs(x = "Dates", y = "RFU")



ag_df_CR %>% 
  group_by(date) %>%
  filter(date >= as.Date("2021-05-01") & date <= as.Date("2021-11-01"))  %>%
  ggplot(aes(x=date)) + 
  geom_path(aes(y=chl,color="Chlorophyll (RFU)")) + 
  geom_path(aes(y=phy,color="Phycocanin (RFU)")) +
    scale_color_manual(values=c("Chlorophyll (RFU)"="darkgreen", "Phycocanin (RFU)"="orange")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle("2021 Chlorophyll V. Phycocanin ") + 
    labs(x = "Dates", y = "RFU (Relative Fluorescence Units)")


  ag_df_CR <- ag_df_CR %>% pad()


ag_df_CR %>% 
  group_by(date) %>%
  filter(date >= as.Date("2015-05-01") & date <= as.Date("2021-11-01"))  %>%
  ggplot(aes(x=date)) + 
  geom_path(aes(y=chl,color="Chlorophyll (RFU)")) + 
  geom_path(aes(y=phy,color="Phycocanin (RFU)")) +
    scale_color_manual(values=c("Chlorophyll (RFU)"="darkgreen", "Phycocanin (RFU)"="orange")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle("< 2021 Chlorophyll V. Phycocanin ") + 
    labs(x = "Dates", y = "RFU (Relative Fluorescence Units)")

ag_df_CR <- na.omit(ag_df_CR)


```

### Plot All EPA Buoy Vars All Time

```{r}
#df_CR
df_CR %>%
  group_by(date, hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity"), mean), .groups = "keep") %>%
  mutate(date = date + hours(hour)) %>%
  ggplot(aes(x = date)) +
  geom_path(aes(y = chl, color = "Chlorophyll (RFU)")) +
  geom_path(aes(y = phy, color = "Phycocanin (RFU)")) +
  geom_path(aes(y = ph, color = "pH")) +
  geom_path(aes(y = Celsius, color = "Temperature (Celsius)")) +
  geom_path(aes(y = spcond, color = "Specific Conductance Ratio (mS/cm)")) +
  geom_path(aes(y = do, color = "Dissolved Oxygen (mg/L)")) +
  geom_path(aes(y = turb, color = "Turbidity (FNU)")) +
  geom_path(aes(y = Salinity, color = "Salinity (ppm)")) +
  scale_color_manual(
    values = c("Chlorophyll (RFU)" = "green",
               "Phycocanin (RFU)" = "orange",
               "pH" = "brown",
               "Temperature (Celsius)" = "red",
               "Specific Conductance Ratio (mS/cm)" = "pink",
               "Dissolved Oxygen (mg/L)" = "yellow",
               "Turbidity (FNU)" = "purple",
               "Salinity (ppm)" = "blue"),
    name = "Color"
  ) + 
      labs(x = "Dates", y = "Units") +
theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle("All EPA Buoy Vars")


ag_df_CR <- ag_df_CR %>%
    mutate(date = as.POSIXct(date, format = "%Y-%m-%d"))
  ag_df_CR <- ag_df_CR %>% pad()
  
#ag_df_CR
ag_df_CR %>%
    mutate(date = as.POSIXct(date, format = "%Y-%m-%d")) %>%
  group_by(date) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity"), mean), .groups = "keep") %>%
  ggplot(aes(x = date)) +
  geom_path(aes(y = chl, color = "Chlorophyll (RFU)")) +
  geom_path(aes(y = phy, color = "Phycocanin (RFU)")) +
  geom_path(aes(y = ph, color = "pH")) +
  geom_path(aes(y = Celsius, color = "Temperature (Celsius)")) +
  geom_path(aes(y = spcond, color = "Specific Conductance Ratio (mS/cm)")) +
  geom_path(aes(y = do, color = "Dissolved Oxygen (mg/L)")) +
  geom_path(aes(y = turb, color = "Turbidity (FNU)")) +
  geom_path(aes(y = Salinity, color = "Salinity (ppm)")) +
  scale_color_manual(
    values = c("Chlorophyll (RFU)" = "green",
               "Phycocanin (RFU)" = "orange",
               "pH" = "brown",
               "Temperature (Celsius)" = "red",
               "Specific Conductance Ratio (mS/cm)" = "pink",
               "Dissolved Oxygen (mg/L)" = "yellow",
               "Turbidity (FNU)" = "purple",
               "Salinity (ppm)" = "blue"),
    name = "Color"
  ) + 
      labs(x = "Dates", y = "Units") +
theme(plot.title = element_text(hjust = 0.5)) +
    ylim(0, 31) +
  ggtitle("2015 - 2023 EPA Buoy Variables")


ag_df_CR <- na.omit(ag_df_CR)


```

####CR BUOY

```{r}
ag_df_CR

ag_df_CR$chl

ag_df_CR$phy

ag_df_CR$ph

ag_df_CR$Celsius

ag_df_CR$spcond

ag_df_CR$do

ag_df_CR$turb

ag_df_CR$Salinity

```

###9:12

```{r}

morndf_CR

morndf_CR$chl

mornddf_CR$phy

mornddf_CR$ph

mornddf_CR$Celsius

mornddf_CR$spcond

mornddf_CR$do

mornddf_CR$turb

mornddf_CR$Salinity


```

#ACFs

```{r}

ag_df_CR
morndf_CR
df_CR



```

###ACF Aggreggated

```{r}
ag_df_CR <- na.omit(ag_df_CR)

#2021
ts_chl_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)


#MORNDF
morndf_chl_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

morndf_phy_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)

length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 24*30, main = " Hourly Chlorophyll ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 24*30, main = "Hourly Phycocanin ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))

acf(ts_chl_2021,lag.max = 30, main = "Daily Chlorophyll ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 30, main = "Daily Phycocanin  ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))

length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 24*30, main = " 9 AM - 12 PM Chlorophyll ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 24*30, main = "9 AM - 12 PM Phycocanin ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))

## you can check an individual value as follows
cor(ts_phy_2021,lag(ts_phy_2021,6),use="pairwise")

df_CR <- na.omit(df_CR)
#2021
ts_chl_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)

length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 24*30, main = " Hourly Chlorophyll ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 24*30, main = "Hourly Phycocanin ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))




```

#PACFs

```{r}

morndf_CR <- na.omit(morndf_CR)
ag_df_CR<- na.omit(ag_df_CR)

#2021
ts_chl_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

ts_phy_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)


#MORNDF
morndf_chl_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(chl)

morndf_phy_2021 <- ag_df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date) %>%
  summarise(across(c("chl","phy"),mean),.groups = "keep") %>%
  pull(phy)


acf(ts_chl_2021,lag.max = 20, main = "Daily Chlorophyll ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 20, main = "Daily Phycocanin  ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))

length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 20, main = " 9 AM - 12 PM Chlorophyll ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 20, main = "9 AM - 12 PM Phycocanin ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))

## you can check an individual value as follows
cor(ts_phy_2021,lag(ts_phy_2021,6),use="pairwise")


#PACF 2021
pacf2021 <- morndf_CR %>% 
  filter(year(date)==2021) %>%
  pull(chl) %>%
  pacf(lag.max = 7 )
plot(pacf2021, main = " 9 AM - 12 PM Chlorophyll PACF")

pacf2021 <- morndf_CR %>% 
  filter(year(date)==2021) %>%
  pull(phy) %>%
  pacf(lag.max= 7)
plot(pacf2021, main = "9 AM - 12 PM Phycocanin PACF")


pacf2021 <- ag_df_CR %>% 
  filter(year(date)==2021) %>%
  pull(chl) %>%
  pacf(lag.max= 7)
plot(pacf2021, main = "Daily Chlorophyll PACF")

pacf2021 <- ag_df_CR %>% 
  filter(year(date)==2021) %>%
  pull(phy) %>%
  pacf(lag.max= 7)
plot(pacf2021, main = "Daily Phyocanin PACF")




```

###HOURLY

```{r}

df_CR


#CHL
acf_chl_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(chl)

#PHY
acf_phy_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(phy)

#ph
acf_ph_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(ph)

#Celsius
acf_Celsius_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(Celsius)

#spcond
acf_spcond_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(spcond)

#spcond
acf_do_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(do)

#turb
acf_turb_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(turb)

#Salinity 
acf_Salinity_2021 <- df_CR %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("chl", "phy", "ph", "Celsius", "spcond", "do", "turb", "Salinity",),mean),.groups = "keep") %>%
  pull(Salinity)


#DO LEGENDS


length(ts_chl_2021)
acf(ts_chl_2021,lag.max = 24*30, main = "Cholorophyll Hourly Non-Aggregated ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 

#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 24*30, main = "Phycocanin Hourly Non-Aggregated ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))

acf(ts_chl_2021,lag.max = 30, main = "Cholorophyll Daily Non-Aggregated ACF")
abline(h = c(0.3,0.6) , col = c("red","red")) #change to lagmax = 30 if want days 
#determine lag -talk to deyle?
acf(ts_phy_2021,lag.max = 30, main = "Phycocanin Daily Non-Aggregated ACF")
abline(h = c(0.3,0.6) , col = c("red","red"))


## you can check an individual value as follows
cor(ts_phy_2021,lag(ts_phy_2021,6),use="pairwise")



#df_CR$chl

#df_CR$phy

#df_CR$ph

#df_CR$Celsius

#df_CR$spcond

#df_CR$do

#df_CR$turb

#df_CR$Salinity


```

##LOGAN

```{r}


#ag_Logan$HourlyAltimeterSetting 


acf_ag_Logan$HourlyAltimeterSetting <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("    ag_Logan$HourlyAltimeterSetting ",
"HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyAltimeterSetting)


     #acf_ag_Logan$HourlyDewPointTemperature 
     
     acf_ag_Logan$HourlyDewPointTemperature <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyDewPointTemperature)
    
     #acf_ag_Logan$HourlyDryBulbTemperature 
     
      acf_ag_Logan$HourlyDryBulbTemperature  <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyDryBulbTemperature )
    
     #acf_ag_Logan$HourlyPrecipitation 
  
   acf_ag_Logan$HourlyPrecipitation  <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyPrecipitation)
    
    #acf_ag_Logan$HourlyRelativeHumidity 
  
   acf_ag_Logan$HourlyRelativeHumidity <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyRelativeHumidity )
   
     #acf_ag_Logan$HourlyStationPressure 
  
   acf_ag_Logan$HourlyStationPressure  <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyStationPressure)
    
     #acf_ag_Logan$HourlyVisibility
  
   acf_ag_Logan$HourlyVisibility <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyVisibility)
    
    #acf_ag_Logan$HourlyWetBulbTemperature 
  
   acf_ag_LoganHourlyWetBulbTemperature <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyWetBulbTemperature )
    
     #acf_ag_Logan$HourlyWindDirection 
  
   acf_ag_Logan$HourlyWindDirection  <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyWindDirection )
    
     #acf_ag_Logan$HourlyWindGustSpeed
  
   acf_ag_Logan$HourlyWindGustSpeed <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyWindGustSpeed)
    
     #acf_ag_Logan$HourlyWindSpeed 
  
   acf_ag_Logan$HourlyWindSpeed <- ag_Logan %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(HourlyWindSpeed)
    
  


```

##MWRA Non-CSO

```{r}

#acf_ag_CR_secchi$`Total Suspended Solids (mg/L)`
 
   acf_ag_CR_secchi$`Total Suspended Solids (mg/L)` <- ag_CR_secchi %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(`Total Suspended Solids (mg/L)`)

#acf_ag_CR_nutrients$`Ammonium (uM)`
 
   acf_ag_CR_nutrients$`Ammonium (uM)` <- ag_CR_nutrients %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(`Ammonium (uM)`)
  
  #acf_ag_CR_nutrients$`Nitrate+nitrite (uM)`
 
   acf_ag_CR_nutrients$`Nitrate+nitrite (uM)` <-ag_CR_nutrients %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(`Nitrate+nitrite (uM)`)
  
  #acf_ag_CR_nutrients$`Phosphate (uM)`
 
   acf_ag_CR_nutrients$`Phosphate (uM)` <- ag_CR_nutrients %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(`Phosphate (uM)`)
  
  #acf_ag_CR_nutrients$`Total phosphorus (uM)`
 
   acf_ag_CR_nutrients$`Total phosphorus (uM)` <- ag_CR_nutrients %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(`Total phosphorus (uM)`)
  
    #acf_ag_CR_nutrients$`Phaeophytin (ug/L)`
 
   acf_ag_CR_nutrients$`Phaeophytin (ug/L)` <- ag_CR_nutrients %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(`Phaeophytin (ug/L)`)
  

  

    #acf_ag_CR_bacteria$Enterococcus

 
 acf_ag_CR_bacteria$Enterococcus <- ag_CR_bacteria %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(Enterococcus)
  
      #acf_ag_CR_bacteria$E_coli

 acf_ag_CR_bacteria$E_coli <- ag_CR_bacteria %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(E_coli)
  
     #acf_ag_CR_bacteria$coliform

 acf_ag_CR_bacteria$coliform <- ag_CR_bacteria %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  summarise(across(c("HourlyDewPointTemperature ", "HourlyDryBulbTemperature ", "HourlyPrecipitation", "HourlyRelativeHumidity", "HourlyStationPressure ", "HourlyVisibility", "HourlyWetBulbTemperature ", "HourlyWindDirection ", "HourlyWindGustSpeed", "HourlyWindSpeed") %>%
  pull(coliform)
  


```

##CSO

```{r}

 #acf_CAM017$MG 

 acf_CAM017$MG <- CAM017 %>% 
  filter(year(date) == 2021) %>%
  group_by(date,hour) %>%
  pull(MG)



```

#ARIMA

## ARIMA Non-Aggregated

```{r}
df_CR <- df_CR %>% pad()

class(df_CR )
df_CR $chl <- as.numeric(df_CR$chl)

#plot(ag_df_CR$date, ag_df_CR$chl) 

#Fit Dataset
rate <- ts(df_CR [,'chl'],start = c(2015,5), frequency = 365 )
#Tell the gaps and days 


#Grab Data
autoplot(rate) + ggtitle ("Autoplot - Non-Aggregated ") + ylab("Chlorophyll (RFU)") + theme(plot.title = element_text(hjust = 0.5))



#Build ARIMA Model - include seasonal autoregressive and seasonal autoregressive moving averages.
fit_ARIMA <-auto.arima(rate, seasonal = TRUE)
print(summary(fit_ARIMA))
checkresiduals(fit_ARIMA)


#Forecast
fcast <- forecast(fit_ARIMA, h =365) #h = amount of periods ahead
autoplot
plot(fcast)
print(summary(fcast))

#Fitting an auto.arima model in R using the Forecast package
#fit_basic1<- auto.arima(df_CR,xreg=trainREG_TS)
#forecast_1<-forecast(fit_basic1,xreg = testREG_TS)
```


#Aggreggated Values

```{r}

#Aggregate Values Daily

ag_df_CR <-df_CR %>%
   group_by(date) %>%
  summarise(chl=mean(chl), phy=mean(phy), ph=mean(ph), Celsius=mean(Celsius), spcond=mean(spcond), do=mean(do), turb=mean(turb), Salinity = mean(Salinity))


```

## ARIMA Aggreggated Daily

```{r}
ag_df_CR <- ag_df_CR  %>% pad()

class(ag_df_CR)
ag_df_CR$chl <- as.numeric(ag_df_CR$chl)

##CHL


#Fit Dataset
rate <- ts(ag_df_CR[,'chl'],start = c(2015,5), frequency = 365 )
#Tell the gaps and days 



#Grab Data
autoplot(rate) + ggtitle ("Autoplot - Daily Aggregate ") + ylab("Chlorophyll (RFU)") + theme(plot.title = element_text(hjust = 0.5))


#Build ARIMA Model - include seasonal autoregressive and seasonal autoregressive moving averages.
fit_ARIMA <-auto.arima(rate, seasonal = TRUE)
print(summary(fit_ARIMA))
checkresiduals(fit_ARIMA)


#Forecast
fcast <- forecast(fit_ARIMA, h =365) #h = amount of periods ahead
autoplot
plot(fcast)
print(summary(fcast))

#Fitting an auto.arima model in R using the Forecast package
#fit_basic1<- auto.arima(df_CR,xreg=trainREG_TS)
#forecast_1<-forecast(fit_basic1,xreg = testREG_TS)


##PHY
p

#Fit Dataset
rate <- ts(ag_df_CR[,'phy'],start = c(2015,5), frequency = 365 )
#Tell the gaps and days 



#Grab Data
autoplot(rate) + ggtitle ("Autoplot - Daily Aggregate ") + ylab("Chlorophyll (RFU)") + theme(plot.title = element_text(hjust = 0.5))



#Build ARIMA Model - include seasonal autoregressive and seasonal autoregressive moving averages.
fit_ARIMA <-auto.arima(rate, seasonal = TRUE)
print(summary(fit_ARIMA))
checkresiduals(fit_ARIMA)


#Forecast
fcast <- forecast(fit_ARIMA, h =365) #h = amount of periods ahead
autoplot
plot(fcast)
print(summary(fcast))

#Fitting an auto.arima model in R using the Forecast package
#fit_basic1<- auto.arima(df_CR,xreg=trainREG_TS)
#forecast_1<-forecast(fit_basic1,xreg = testREG_TS)



```

#COEFFICENTS OF CORRELATION

#REGRESSIONS

```{r}

ag_df_CR %>% 
  ggplot(aes(x=ph, y=phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(phy), color = "Mean Phy Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = mean(ph), color = "Mean Ph Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Mean Phy Trendline" = "blue", 
                                 "Best Fit Line" = "purple", 
                                 "Mean Ph Trendline" = "orange"), 
                     breaks = c("Points", "Mean Phy Trendline", 
                                "Best Fit Line", "Mean Ph Trendline"),
                     labels = c("Points", "Mean Phy Trendline", 
                                "Best Fit Line", "Mean Ph Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA),
    linetype = c("blank", "dotted", "solid", "dotted")
  ))) +
  ggtitle("pH vs. Phycocanin (RFU)") +
  labs(color = "Legend",
       x = "pH",
       y = "Phycocanin (RFU")


ag_df_CR %>% 
  ggplot(aes(x=ph, y=phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(phy), color = "Mean Phycocanin Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = mean(ph), color = "Mean pH Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Mean pH Trendline" = "blue", 
                                 "Best Fit Line" = "purple", 
                                 "Mean Phycocanin Trendline" = "orange"), 
                     breaks = c("Points", "Mean Phycocanin Trendline", 
                                "Best Fit Line", "Mean pH Trendline"),
                     labels = c("Points", "Mean Phycocanin Trendline", 
                                "Best Fit Line", "Mean pH Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA),
    linetype = c("blank", "dotted", "solid", "dotted")
  ))) +
  ggtitle("pH vs. Phycocanin (RFU)") +
  labs(color = "Legend",
       x = "pH",
       y = "Phycocanin (RFU")



```

##PLOTS W/ CORR \> 0.5

```{r}
phphy
dochl
turbphy



ag_df_CR %>% 
  ggplot(aes(x=ph, y=phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", ) +
  geom_vline(aes(xintercept = mean(ag_df_CR$ph), color = "Ph Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$ph), color = "Ph Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Ph Mean Trendline" = "orange", "Ph Median Trendline" = "brown"), 
                     breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline"),
                     labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA, NA, NA),
    linetype = c(1, 0, 0, 0, 0 ,0)
  ))) +
  ggtitle("Ph vs. Phy") +
  labs(color = "Legend Title")






```

#PLOTS

```{r}

ag_df_CR <- na.omit(ag_df_CR)
ag_Logan <- na.omit(ag_Logan)
ag_CR_nutrients
ag_CR_secchi
ag_CR_bacteria


#ag_CR_secchi

ag_CR_secchi$`Total Suspended Solids (mg/L)`

#ag_CR_nutrients 

ag_CR_nutrients$`Ammonium (uM)`
ag_CR_nutrients$`Nitrate+nitrite (uM)`
ag_CR_nutrients$`Phosphate (uM)`
ag_CR_nutrients$`Total phosphorus (uM)`
ag_CR_nutrients$`Phaeophytin (ug/L)`

#ag_CR_bacteria

ag_CR_bacteria$Enterococcus
ag_CR_bacteria$E_coli
ag_CR_bacteria$coliform


#Ph MEDIAN AND MEAN ARE THE SAME?


#PH VS. PHY

ag_df_CR %>% 
  ggplot(aes(x=ph, y=phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", ) +
  geom_vline(aes(xintercept = mean(ag_df_CR$ph), color = "Ph Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$ph), color = "Ph Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Ph Mean Trendline" = "orange", "Ph Median Trendline" = "brown"), 
                     breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline"),
                     labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA, NA, NA),
    linetype = c(1, 0, 0, 0, 0 ,0)
  ))) +
  ggtitle("Ph vs. Phy") +
  labs(color = "Legend Title")

#PH VS. CHL


ag_df_CR %>% 
  ggplot(aes(x=ph, y=chl, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", ) +
  geom_vline(aes(xintercept = mean(ag_df_CR$ph), color = "Ph Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$ph), color = "Ph Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Chl Mean Trendline" = "blue", "Chl Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Ph Mean Trendline" = "orange", "Ph Median Trendline" = "brown"), 
                     breaks = c("Points", "Chl Mean Trendline", "Chl Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline"),
                     labels = c("Points", "Chl Mean Trendline", "Chl Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA, NA, NA),
    linetype = c(1, 1, 1, 1, 1 ,1)
  ))) +
  ggtitle("Ph vs. Chl") +
  labs(color = "Legend Title")


# Ph vs. Del_phy
ag_df_CR %>% 
  ggplot(aes(x=ph, y=del_phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
  geom_vline(aes(xintercept = mean(ag_df_CR$ph), color = "Ph Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$ph), color = "Ph Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Del_phy Mean Trendline" = "blue", "Del_phy Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Ph Mean Trendline" = "orange", "Ph Median Trendline" = "brown"), 
                     breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline"),
                     labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline", 
                                "Best Fit Line", "Ph Mean Trendline", "Ph Median Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA, NA, NA),
    linetype = c(0, 0, 0, 0, 1, 1)
  ))) +
  ggtitle("Ph vs. Del_phy") +
  labs(color = "Legend Title")


# Chl vs. Phy
ag_df_CR %>% 
  ggplot(aes(x=chl, y=phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
  geom_vline(aes(xintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Chl Mean Trendline" = "orange", "Chl Median Trendline" = "brown"), 
                     breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Chl Mean Trendline", "Chl Median Trendline"),
                     labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Chl Mean Trendline", "Chl Median Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA, NA, NA),
    linetype = c(0, 1, 1, 1, 1 ,1)
  ))) +
  ggtitle("Chl vs. Phy") +
  labs(color = "Legend Title")

# Celsius vs. Phy
ag_df_CR %>% 
  ggplot(aes(x=Celsius, y=phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
  geom_vline(aes(xintercept = mean(ag_df_CR$Celsius), color = "Celsius Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$Celsius), color = "Celsius Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Celsius Mean Trendline" = "orange", "Celsius Median Trendline" = "brown"), 
                     breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Celsius Mean Trendline", "Celsius Median Trendline"),
                     labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline", 
                                "Best Fit Line", "Celsius Mean Trendline", "Celsius Median Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA, NA, NA),
    linetype = c(0, 1, 1, 1, 1 ,1)
  ))) +
  ggtitle("Celsius vs. Phy") +
  labs(color = "Legend Title")

# Celsius vs. Chl
ag_df_CR %>% 
  ggplot(aes(x=Celsius, y=chl, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
  geom_vline(aes(xintercept = mean(ag_df_CR$Celsius), color = "Celsius Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$Celsius), color = "Celsius Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Chl Mean Trendline" = "blue", "Chl Median Trendline" = "green",
"Best Fit Line" = "purple",
"Celsius Mean Trendline" = "orange", "Celsius Median Trendline" = "brown"),
breaks = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Celsius Mean Trendline", "Celsius Median Trendline"),
labels = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Celsius Mean Trendline", "Celsius Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Celsius vs. Chl") +
labs(color = "Legend Title")


#Celsius vs. Del_phy

ag_df_CR %>%
ggplot(aes(x=Celsius, y=del_phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$Celsius), color = "Celsius Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$Celsius), color = "Celsius Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Del_phy Mean Trendline" = "blue", "Del_phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Celsius Mean Trendline" = "orange", "Celsius Median Trendline" = "brown"),
breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Celsius Mean Trendline", "Celsius Median Trendline"),
labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Celsius Mean Trendline", "Celsius Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Celsius vs. Del_phy") +
labs(color = "Legend Title")

#Spcond vs. Phy
ag_df_CR %>%
ggplot(aes(x=spcond, y=phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$spcond), color = "Spcond Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$spcond), color = "Spcond Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Spcond Mean Trendline" = "orange", "Spcond Median Trendline" = "brown"),
breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Spcond Mean Trendline", "Spcond Median Trendline"),
labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Spcond Mean Trendline", "Spcond Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 1, 1, 1, 1 ,1)
))) +
ggtitle("Spcond vs. Phy") +
labs(color = "Legend Title")

#Spcond vs. Chl
ag_df_CR %>%
ggplot(aes(x=spcond, y=chl, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$spcond), color = "Spcond Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$spcond), color = "Spcond Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Chl Mean Trendline" = "blue", "Chl Median Trendline" = "green",
"Best Fit Line" = "purple",
"Spcond Mean Trendline" = "orange", "Spcond Median Trendline" = "brown"),
breaks = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Spcond Mean Trendline", "Spcond Median Trendline"),
labels = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Spcond Mean Trendline", "Spcond Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Spcond vs. Chl") +
labs(color = "Legend Title")


#Spcond vs. Del_phy

ag_df_CR %>%
ggplot(aes(x=spcond, y=del_phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$spcond), color = "Spcond Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$spcond), color = "Spcond Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Del_phy Mean Trendline" = "blue", "Del_phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Spcond Mean Trendline" = "orange", "Spcond Median Trendline" = "brown"),
breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Spcond Mean Trendline", "Spcond Median Trendline"),
labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Spcond Mean Trendline", "Spcond Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Spcond vs. Del_phy") +
labs(color = "Legend Title")

#Do vs. Phy
ag_df_CR %>%
ggplot(aes(x=do, y=phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$do), color = "Do Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$do), color = "Do Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Do Mean Trendline" = "orange", "Do Median Trendline" = "brown"),
breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Do Mean Trendline", "Do Median Trendline"),
labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Do Mean Trendline", "Do Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 1, 1, 1, 1 ,1)
))) +
ggtitle("Do vs. Phy") +
labs(color = "Legend Title")

#Do vs. Chl
ag_df_CR %>%
ggplot(aes(x=do, y=chl, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$do), color = "Do Mean Trendline"), linetype = "dashed
") +
geom_vline(aes(xintercept = median(ag_df_CR$do), color = "Do Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Chl Mean Trendline" = "blue", "Chl Median Trendline" = "green",
"Best Fit Line" = "purple",
"Do Mean Trendline" = "orange", "Do Median Trendline" = "brown"),
breaks = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Do Mean Trendline", "Do Median Trendline"),
labels = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Do Mean Trendline", "Do Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Do vs. Chl") +
labs(color = "Legend Title")

#Do vs. Del_phy
ag_df_CR %>%
ggplot(aes(x=do, y=del_phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$do), color = "Do Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$do), color = "Do Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Del_phy Mean Trendline" = "blue", "Del_phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Do Mean Trendline" = "orange", "Do Median Trendline" = "brown"),
breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Do Mean Trendline", "Do Median Trendline"),
labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Do Mean Trendline", "Do Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Do vs. Del_phy") +
labs(color = "Legend Title")

#Turb vs. Chl
ag_df_CR %>%
ggplot(aes(x=turb, y=chl, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$turb), color = "Turb Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$turb), color = "Turb Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Chl Mean Trendline" = "blue", "Chl Median Trendline" = "green",
"Best Fit Line" = "purple",
"Turb Mean Trendline" = "orange", "Turb Median Trendline" = "brown"),
breaks = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Turb Mean Trendline", "Turb Median Trendline"),
labels = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Turb Mean Trendline", "Turb Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Turb vs. Chl") +
labs(color = "Legend Title")


#Turb vs. Phy
ag_df_CR %>%
ggplot(aes(x=turb, y=phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$turb), color = "Turb Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$turb), color = "Turb Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Turb Mean Trendline" = "orange", "Turb Median Trendline" = "brown"),
breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Turb Mean Trendline", "Turb Median Trendline"),
labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Turb Mean Trendline", "Turb Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 1, 1, 1, 1 ,1)
))) +
ggtitle("Turb vs. Phy") +
labs(color = "Legend Title")

#Turb vs. Del_phy
ag_df_CR %>%
ggplot(aes(x=turb, y=del_phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$turb), color = "Turb Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$turb), color = "Turb Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Del_phy Mean Trendline" = "blue", "Del_phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Turb Mean Trendline" = "orange", "Turb Median Trendline" = "brown"),
breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Turb Mean Trendline", "Turb Median Trendline"),
labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Turb Mean Trendline", "Turb Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 1, 1, 1, 1 ,1)
))) +
ggtitle("Turb vs. Del_phy") +
labs(color = "Legend Title")

#Salinity vs. Phy
ag_df_CR %>%
ggplot(aes(x=Salinity, y=phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$Salinity), color = "Salinity Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$Salinity), color = "Salinity Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Phy Mean Trendline" = "blue", "Phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Salinity Mean Trendline" = "orange", "Salinity Median Trendline" = "brown"),
breaks = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Salinity Mean Trendline", "Salinity Median Trendline"),
labels = c("Points", "Phy Mean Trendline", "Phy Median Trendline",
"Best Fit Line", "Salinity Mean Trendline", "Salinity Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Salinity vs. Phy") +
labs(color = "Legend Title")

#Salinity vs. Chl
ag_df_CR %>%
ggplot(aes(x=Salinity, y=chl, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$Salinity), color = "Salinity Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$Salinity), color = "Salinity Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Chl Mean Trendline" = "blue", "Chl Median Trendline" = "green",
"Best Fit Line" = "purple",
"Salinity Mean Trendline" = "orange", "Salinity Median Trendline" = "brown"),
breaks = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Salinity Mean Trendline", "Salinity Median Trendline"),
labels = c("Points", "Chl Mean Trendline", "Chl Median Trendline",
"Best Fit Line", "Salinity Mean Trendline", "Salinity Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Salinity vs. Chl") +
labs(color = "Legend Title")



#Salinity vs. Del_phy

ag_df_CR %>%
ggplot(aes(x=Salinity, y=del_phy, color = "Points")) +
geom_point() +
geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
geom_vline(aes(xintercept = mean(ag_df_CR$Salinity), color = "Salinity Mean Trendline"), linetype = "dashed") +
geom_vline(aes(xintercept = median(ag_df_CR$Salinity), color = "Salinity Median Trendline"), linetype = "dashed") +
scale_color_manual(values = c("Points" = "red",
"Del_phy Mean Trendline" = "blue", "Del_phy Median Trendline" = "green",
"Best Fit Line" = "purple",
"Salinity Mean Trendline" = "orange", "Salinity Median Trendline" = "brown"),
breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Salinity Mean Trendline", "Salinity Median Trendline"),
labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline",
"Best Fit Line", "Salinity Mean Trendline", "Salinity Median Trendline")) +
guides(color = guide_legend(override.aes = list(
shape = c(19, NA, NA, NA, NA, NA),
linetype = c(0, 0, 0, 1, 1 ,1)
))) +
ggtitle("Salinity vs. Del_phy") +
labs(color = "Legend Title")


# Phy vs. Chl
ag_df_CR %>% 
  ggplot(aes(x=phy, y=chl, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
  geom_vline(aes(xintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Chl Mean Trendline" = "blue", "Chl Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Phy Mean Trendline" = "orange", "Phy Median Trendline" = "brown"), 
                     # breaks = c("Points", "Chl Mean Trendline", "Chl Median Trendline", 
                     #            "Best Fit Line", "Phy Mean Trendline", "Phy Median Trendline"),
                     labels = c("Points", "Chl Mean Trendline", "Chl Median Trendline", 
                                "Best Fit Line", "Phy Mean Trendline", "Phy Median Trendline")) +
  guides(color = guide_legend(override.aes = list(
    shape = c(19, NA, NA, NA, NA, NA),
    linetype = c(0, 0, 0, 1, 1 ,1)
  ))) +
  ggtitle("Phy vs. Chl") +
  labs(color = "Legend Title")

# Phy vs. Del_phy
ag_df_CR %>% 
  ggplot(aes(x=phy, y=del_phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
  geom_vline(aes(xintercept = mean(ag_df_CR$phy), color = "Phy Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$phy), color = "Phy Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Del_phy Mean Trendline" = "blue", "Del_phy Median Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Phy Mean Trendline" = "orange", "Phy Median Trendline" = "brown"), 
                     breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline", 
                                "Best Fit Line", "Phy Mean Trendline", "Phy Median Trendline"),
                     labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline", 
                                "Best Fit Line", "Phy Mean Trendline", "Phy Median Trendline")) +
  # guides(color = guide_legend(override.aes = list(
  #   shape = c(19, NA, NA, NA, NA, NA),
  #   linetype = c(0, 0, 0, 1, 1 ,1)
  # ))) +
  ggtitle("Phy vs. Del_phy") +
  labs(color = "Legend Title")

# Chl vs. Del_phy
ag_df_CR %>% 
  ggplot(aes(x=chl, y=del_phy, color = "Points")) + 
  geom_point() +
  geom_hline(aes(yintercept = mean(ag_df_CR$del_phy), color = "Del_phy Mean Trendline"), linetype = "dashed") +
  geom_hline(aes(yintercept = median(ag_df_CR$del_phy), color = "Del_phy Median Trendline"), linetype = "dashed") +
  geom_smooth(aes(color = "Best Fit Line"), method = "lm", se = FALSE) +
  geom_vline(aes(xintercept = mean(ag_df_CR$chl), color = "Chl Mean Trendline"), linetype = "dashed") +
  geom_vline(aes(xintercept = median(ag_df_CR$chl), color = "Chl Median Trendline"), linetype = "dashed") +
  scale_color_manual(values = c("Points" = "red", 
                                 "Del_phy Mean Trendline" = "blue", "Del_phy Mean Trendline" = "green", 
                                 "Best Fit Line" = "purple", 
                                 "Chl Mean Trendline" = "orange", "Chl Median Trendline" = "brown"), 
                     breaks = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline", 
                                "Best Fit Line", "Chl Mean Trendline", "Chl Median Trendline"),
                     labels = c("Points", "Del_phy Mean Trendline", "Del_phy Median Trendline", 
                                "Best Fit Line", "Chl Mean Trendline", "Chl Median Trendline")) +
  # guides(color = guide_legend(override.aes = list(
  #   shape = c(19, NA, NA, NA, NA, NA),
  #   linetype = c(0, 0, 0, 1, 1 ,1)
  # ))) +
  ggtitle("Chl vs. Del_phy") +
  labs(color = "Legend Title")





#median: do 0.5 quantile regression




```



#   TABLED (TBD)



#HISTOGRAM

ccm uses y to predict x, if true, x can affect y ccm wraps (Simplex
target = x, columns = y)

multivariate Simplex ( Embedded = True, columns = c("x1, "x2)) set CCM
samples to 10 to see result


#PULL GRAPHS

```{r}
plots.dir.path <- list.files(tempdir("C:\\Users\\mfman\\AppData\\Local\\Temp\\RtmpaE80Ug"), pattern="rs-graphics", full.names = TRUE); 
plots.png.paths <- list.files(plots.dir.path, pattern=".png", full.names = TRUE)
```

```{r}
file.copy(from=plots.png.paths, to="C:/Users/mfman/OneDrive/Desktop/HAB_PLOTS")

```




#MULTIVAR 




### Muiltivariate S-Map

-   rho_theta_e3

    -   Theta

    -   Rho

```{r}

rho_theta_e3 = PredictNonlinear(dataFrame = ag_df_CR, columns = "chl",
target = "chl", lib = lib_ins, pred = lib_ins, E = 4)

```

### **Evaluate Simplex Prediction** - out of sample forecasting (figure 5) 

-   ag_df_CRPredict

    -   Observations

    -   Predictions

    -   Pred_Variance

```{r}

ag_df_CRPredict <- Simplex(dataFrame = ag_df_CR,lib = lib_ins, pred = lib_ins, pred = "1076 1223", target = "chl",
columns = "chl", E = 4)

#S-Map = Theta



```

```{r}

 ComputeError(ag_df_CRPredict$Observations, ag_df_CRPredict$Predictions)
 
```

### Evaluate S-Map - Multivar 

It can be advantageous to combine different time series to create the
phase-space embedding, providing they are observed from the same system.

-   Smap

    -   predictions

    -   coefficents

    -   singularvalues

    -   chl/chl(t-1,2,3,4)

**#Where does TentMapNoise come from? SMapPredict?**

**Tentmap Noise = Theta?**

**What is columns?**

```{r}

 #If = 0, all library points have the same weight regardless of the local state of the predictee; 

smap = SMap(dataFrame = ag_df_CR, lib = lib_ins, pred = lib_ins, target = "chl",
columns = "chl", E = 4, theta = 5)

#if h > , the forecast given by the S-map depends on the local state of the predictee, and thus produces locally different fittings.
#smap = SMap(dataFrame = ag_df_CR, lib = "1 1075", pred = "1076 1223", target = "chl",
#columns = "chl", E = 2, theta = 0)

```

```{r}
head(cbind(smap$predictions, smap$coefficients), 2)

tail(cbind(smap$predictions, smap$coefficients))


```


#   CROSSMAP

###CCM EPA BUOY
```{r}
ag_df_CR <- na.omit(ag_df_CR)

```



##PH

```{r}

tau_i <- 6

ag_df_CR <- readRDS("C:\\Users\\mfman\\OneDrive\\Desktop\\HAB2\\HAB2\\1)LIB\\ag_df_CR.rds")
ag_df_CR <- na.omit(ag_df_CR)

library(rEDM)

#No "Includeddata = TRUE"

#CMAPS

#cmap.ph.del_phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "ph", target = #"del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE)

cmap.ph.phy <- CCM(dataFrame = ag_df_CR, E = 6, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE)  #start end space in between

cmap.ph.chl <- CCM(dataFrame = ag_df_CR, E = 6, tau=-7, Tp = 0, columns = "ph", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 



#Surrogates
# 
# Surr.cmap.ph.phy <- CCM(dataFrame = Surrogate, E = 2, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

#Surr.cmap.ph.chl <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "chl", target # = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# Surr.cmap.ph.chl <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "ph", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 


#lib_sizes = "1169"
#sample = "100"
#random=FALSE


#CMAP Correlations 

#ph.del_phy.corr <- cor(cmap.ph.del_phy)
#ph.del_phy.corr <- ph.del_phy.corr[1, 3]

ph.phy.corr <- cor(cmap.ph.phy)
ph.phy.corr <- ph.phy.corr[1, 3]

ph.chl.corr <- cor(cmap.ph.chl)
ph.chl.corr <- ph.chl.corr[1, 3]

#Surrogate Correlations 

Surr.ph.del_phy.corr <- cor(Surr.cmap.ph.del_phy)
Surr.ph.del_phy.corr <- Surr.ph.del_phy.corr[1, 3]

Surr.ph.phy.corr <- cor(Surr.cmap.ph.phy)
Surr.ph.phy.corr <- Surr.ph.phy.corr[1, 3]

Surr.ph.chl.corr <- cor(Surr.cmap.ph.chl)
Surr.ph.chl.corr <- Surr.ph.chl.corr[1, 3]

#CMAP PLOTS
# 
# #ph.del
# plot(x = cmap.ph.del[,1], y = cmap.ph.del[,2], type = "l",
#      main = "Ph V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
# lines(x = cmap.ph.del[,1], y = cmap.ph.del[,3], col = "red")
# abline(h = ph.del.corr, col = "green", lty = 2)
# legend("topright", legend = c(colnames(cmap.ph.del)[2:3], "Correlation"), 
#        col = c("blue", "red", "green"), lty = c(1, 1, 2))
#ph.phy

cmap.ph.phy.plot <- plot(x = cmap.ph.phy[,1], y = cmap.ph.phy[,3], type = "l",
     main = "Ph V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.ph.phy[,1], y = cmap.ph.phy[,3], col = "red")
lines(x = cmap.ph.phy[,1], y = cmap.ph.phy[,2], col = "blue")
abline(h = (abs(ph.phy.corr)), col = "green", lty = 2)
abline(h = critical.r(1189), col = "darkgreen", lty = 2)
legend("topright", legend = c(colnames(cmap.ph.phy)[2:3], "Correlation", 
                              "Critical Correlation"), 
       col = c("blue", "red", "green","darkgreen"), lty = c(1, 1, 2,2))


#ph.chl

plot(x = cmap.ph.chl[,1], y = cmap.ph.chl[,2], type = "l",
     main = "Ph V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.ph.chl[,1], y = cmap.ph.chl,3], col = "red")
abline(h = ph.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.ph.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))


#Surrogate Plots
# 
# 
# #ph.del
# plot(x = Surr.cmap.ph.del[,1], y = Surr.cmap.ph.del[,2], type = "l",
#      main = "Ph V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
# lines(x = Surr.cmap.ph.del[,1], y = Surr.cmap.ph.del[,3], col = "red")
# abline(h = Surr.ph.del.corr, col = "green", lty = 2)
# legend("topright", legend = c(colnames(Surr.cmap.ph.del)[2:3], "Correlation"),
#        col = c("blue", "red", "green"), lty = c(1, 1, 2))
#ph.phy
plot(x = Surr.cmap.ph.phy[,1], y = Surr.cmap.ph.phy[,2], type = "l",
     main = "Ph V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.ph.phy[,1], y = Surr.cmap.ph.phy[,3], col = "red")
abline(h = Surr.ph.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.ph.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

#ph.chl

plot(x = Surr.cmap.ph.chl[,1], y = Surr.cmap.ph.chl[,2], type = "l",
     main = "Ph V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.ph.chl[,1], y = Surr.cmap.ph.chl,3], col = "red")
abline(h = Surr.ph.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.ph.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))


#CMAP INCLUDE DATA

#CMAP 
# 
# cmap.ph.del_phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "ph", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.ph.phy2 <- CCM(dataFrame = ag_df_CR, E = 6, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE, includeData = TRUE)  #start end space in between

  
  # CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.ph.chl2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "ph", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

#Surrogates
# 
# Surr.cmap.del_ph.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "ph", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.ph.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.ph.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "ph", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)


#LIBMEAN PLOT

 #PHY
 
  cmap.ph.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`ph:phy`,color="ph:phy")) +
  geom_line(aes(y=`phy:ph`,color="phy:ph")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$ph,ag_df_CR$phy)),lty=2) #CORR of REG?
  
#DEL_PHY
# 
#  cmap.ph.del_phy2$LibMeans %>% 
#   ggplot(aes(x=LibSize)) +
#   geom_line(aes(y=`ph:phy`,color="ph:del_phy")) +
#   geom_line(aes(y=`phy:ph`,color="del_phy:ph")) +
#   geom_hline(aes(yintercept = cor(ag_df_CR$ph,ag_df_CR$del_phy)),lty=2)
 
 
#CHL
 
 cmap.ph.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`ph:phy`,color="ph:chl")) +
  geom_line(aes(y=`phy:ph`,color="chl:ph")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$ph,ag_df_CR$chl)),lty=2)
 
 
 #Surrogate PHY
 
  Surr.cmap.ph.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`ph:phy`,color="ph:phy")) +
  geom_line(aes(y=`phy:ph`,color="phy:ph")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$ph,ag_df_CR$phy)),lty=2)
  
# #Surrogate DEL_PHY
# 
#  Surr.cmap.ph.del_phy2$LibMeans %>% 
#   ggplot(aes(x=LibSize)) +
#   geom_line(aes(y=`ph:phy`,color="ph:del_phy")) +
#   geom_line(aes(y=`phy:ph`,color="del_phy:ph")) +
#   geom_hline(aes(yintercept = cor(ag_df_CR$ph,ag_df_CR$del_phy)),lty=2)
 
 
#Surrogate CHL
 
 Surr.cmap.ph.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`ph:phy`,color="ph:chl")) +
  geom_line(aes(y=`phy:ph`,color="chl:ph")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$ph,ag_df_CR$chl)),lty=2)
 
 
 
#PREDICTSTAT PLOT: Rho V. LibSize 

cmap.ph.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")
# 
# cmap.ph.del_phy2$CCM1_PredictStat %>%
#   ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
#   geom_jitter() + stat_summary(fun = median,geom="line")


cmap.ph.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

#PREDICTSTAT PLOT

Surr.cmap.ph.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")
# 
# Surr.cmap.ph.del_phy2$CCM1_PredictStat %>%
#   ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
#   geom_jitter() + stat_summary(fun = median,geom="line")


Surr.cmap.ph.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")


#EMBED DIMENSION 


#EmbedDimension(dataFrame = ag_df_CR,Tp = 0, columns = "ph",
               #target = "phy",lib="1 1174",pred="1 1174",
               #tau=-7)


#EmbedDimension(dataFrame = ag_df_CR,Tp = 0, columns = "ph",
               #target = "del_phy",lib="1 1174",pred="1 1174",
               #tau=-7)

#EmbedDimension(dataFrame = ag_df_CR,Tp = 0, columns = "ph",
               #target = "chl",lib="1 1174",pred="1 1174",
               #tau=-7)


#EmbedDimension(dataFrame = Surrogate,Tp = 0, columns = "ph",
               #target = "phy",lib="1 1174",pred="1 1174",
               #tau=-7)


#EmbedDimension(dataFrame = Surrogate,Tp = 0, columns = "ph",
               #target = "del_phy",lib="1 1174",pred="1 1174",
               #tau=-7)

#EmbedDimension(dataFrame = Surrogate,Tp = 0, columns = "ph",
               #target = "chl",lib="1 1174",pred="1 1174",
               #tau=-7)




```



##Celsius

```{r}


cmap.Celsius.phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.Celsius.del_phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.Celsius.chl <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Celsius"", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 


Surr.cmap.Celsius.phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.Celsius.del_phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.Celsius.chl <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Celsius"", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# CMAP Correlations
Celsius.phy.corr <- cor(cmap.Celsius.phy)
Celsius.phy.corr <- Celsius.phy.corr[1, 3]

Celsius.del_phy.corr <- cor(cmap.Celsius.del_phy)
Celsius.del_phy.corr <- Celsius.del_phy.corr[1, 3]

Celsius.chl.corr <- cor(cmap.Celsius.chl)
Celsius.chl.corr <- Celsius.chl.corr[1, 3]

# Surrogate Correlations
Surr.Celsius.phy.corr <- cor(Surr.cmap.Celsius.phy)
Surr.Celsius.phy.corr <- Surr.Celsius.phy.corr[1, 3]

Surr.Celsius.del_phy.corr <- cor(Surr.cmap.Celsius.del_phy)
Surr.Celsius.del_phy.corr <- Surr.Celsius.del_phy.corr[1, 3]

Surr.Celsius.chl.corr <- cor(Surr.cmap.Celsius.chl)
Surr.Celsius.chl.corr <- Surr.Celsius.chl.corr[1, 3]

# CMAP PLOTS
# Celsius.phy
plot(x = cmap.Celsius.phy[,1], y = cmap.Celsius.phy[,2], type = "l",
     main = "Celsius V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.Celsius.phy[,1], y = cmap.Celsius.phy[,3], col = "red")
abline(h = Celsius.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.Celsius.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Celsius.del_phy
plot(x = cmap.Celsius.del_phy[,1], y = cmap.Celsius.del_phy[,2], type = "l",
     main = "Celsius V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.Celsius.del_phy[,1], y = cmap.Celsius.del_phy[,3], col = "red")
abline(h = Celsius.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.Celsius.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Celsius.chl
plot(x = cmap.Celsius.chl[,1], y = cmap.Celsius.chl[,2], type = "l",
     main = "Celsius V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.Celsius.chl[,1], y = cmap.Celsius.chl[,3], col = "red")
abline(h = Celsius.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.Celsius.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate PLOTS
# Surrogate Celsius.phy
plot(x = Surr.cmap.Celsius.phy[,1], y = Surr.cmap.Celsius.phy[,2], type = "l",
     main = "Celsius V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.Celsius.phy[,1], y = Surr.cmap.Celsius.phy[,3], col = "red")
abline(h = Surr.Celsius.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.Celsius.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate Celsius.del_phy
plot(x = Surr.cmap.Celsius.del_phy[,1], y = Surr.cmap.Celsius.del_phy[,2], type = "l",
     main = "Celsius V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.Celsius.del_phy[,1], y = Surr.cmap.Celsius.del_phy[,3], col = "red")
abline(h = Surr.Celsius.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.Celsius.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate Celsius.chl
plot(x = Surr.cmap.Celsius.chl[,1], y = Surr.cmap.Celsius.chl[,2], type = "l",
     main = "Celsius V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.Celsius.chl[,1], y = Surr.cmap.Celsius.chl[,3], col = "red")
abline(h = Surr.Celsius.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.Celsius.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# CMAP INCLUDE DATA
# CMAP 
cmap.Celsius.phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.Celsius.del_phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.Celsius.chl2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# Surrogates
Surr.cmap.Celsius.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.Celsius.del_phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.Celsius.chl2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Celsius", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# LIBMEAN PLOT
# PHY
cmap.Celsius.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Celsius:phy`,color="Celsius:phy")) +
  geom_line(aes(y=`phy:Celsius`,color="phy:Celsius")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Celsius,ag_df_CR$phy)),lty=2)
  
# DEL_PHY
cmap.Celsius.del_phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Celsius:phy`,color="Celsius:del_phy")) +
  geom_line(aes(y=`del_phy:Celsius`,color="del_phy:Celsius")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Celsius,ag_df_CR$del_phy)),lty=2)
 
# CHL
cmap.Celsius.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Celsius:phy`,color="Celsius:chl")) +
  geom_line(aes(y=`chl:Celsius`,color="chl:Celsius")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Celsius,ag_df_CR$chl)),lty=2)

# Surrogate PHY
Surr.cmap.Celsius.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Celsius:phy`,color="Celsius:phy")) +
  geom_line(aes(y=`phy:Celsius`,color="phy:Celsius")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Celsius,ag_df_CR$phy)),lty=2)
  
# Surrogate DEL_PHY
Surr.cmap.Celsius.del_phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Celsius:phy`,color="Celsius:del_phy")) +
  geom_line(aes(y=`del_phy:Celsius`,color="del_phy:Celsius")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Celsius,ag_df_CR$del_phy)),lty=2)
 
# Surrogate CHL
Surr.cmap.Celsius.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Celsius:phy`,color="Celsius:chl")) +
  geom_line(aes(y=`chl:Celsius`,color="chl:Celsius")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Celsius,ag_df_CR$chl)),lty=2)


# PREDICTSTAT PLOT
cmap.Celsius.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

cmap.Celsius.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

cmap.Celsius.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# PREDICTSTAT PLOT
Surr.cmap.Celsius.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

Surr.cmap.Celsius.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

Surr.cmap.Celsius.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# EMBED DIMENSION
# EmbedDimension for PHY
EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "Celsius",
               target = "phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for DEL_PHY
EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "Celsius",
               target = "del_phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for CHL
EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "Celsius",
               target = "chl", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for Surrogate PHY
EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "Celsius",
               target = "phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for Surrogate DEL_PHY
EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "Celsius",
               target = "del_phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for Surrogate CHL
EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "Celsius",
               target = "chl", lib = "1 1174", pred = "1 1174",
               tau = -7)


```

##SPCOND

```{r}


cmap.spcond.phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.spcond.del_phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.spcond.chl <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "spcond"", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 


Surr.cmap.spcond.phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.spcond.del_phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.spcond.chl <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# CMAP Correlations
spcond.phy.corr <- cor(cmap.spcond.phy)
spcond.phy.corr <- spcond.phy.corr[1, 3]

spcond.del_phy.corr <- cor(cmap.spcond.del_phy)
spcond.del_phy.corr <- spcond.del_phy.corr[1, 3]

spcond.chl.corr <- cor(cmap.spcond.chl)
spcond.chl.corr <- spcond.chl.corr[1, 3]

# Surrogate Correlations
Surr.spcond.phy.corr <- cor(Surr.cmap.spcond.phy)
Surr.spcond.phy.corr <- Surr.spcond.phy.corr[1, 3]

Surr.spcond.del_phy.corr <- cor(Surr.cmap.spcond.del_phy)
Surr.spcond.del_phy.corr <- Surr.spcond.del_phy.corr[1, 3]

Surr.spcond.chl.corr <- cor(Surr.cmap.spcond.chl)
Surr.spcond.chl.corr <- Surr.spcond.chl.corr[1, 3]

# CMAP PLOTS
# spcond.phy
plot(x = cmap.spcond.phy[,1], y = cmap.spcond.phy[,2], type = "l",
     main = "spcond V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.spcond.phy[,1], y = cmap.spcond.phy[,3], col = "red")
abline(h = spcond.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.spcond.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# spcond.del_phy
plot(x = cmap.spcond.del_phy[,1], y = cmap.spcond.del_phy[,2], type = "l",
     main = "spcond V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.spcond.del_phy[,1], y = cmap.spcond.del_phy[,3], col = "red")
abline(h = spcond.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.spcond.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# spcond.chl
plot(x = cmap.spcond.chl[,1], y = cmap.spcond.chl[,2], type = "l",
     main = "spcond V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.spcond.chl[,1], y = cmap.spcond.chl[,3], col = "red")
abline(h = spcond.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.spcond.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate PLOTS
# Surrogate spcond.phy
plot(x = Surr.cmap.spcond.phy[,1], y = Surr.cmap.spcond.phy[,2], type = "l",
     main = "spcond V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.spcond.phy[,1], y = Surr.cmap.spcond.phy[,3], col = "red")
abline(h = Surr.spcond.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.spcond.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate spcond.del_phy
plot(x = Surr.cmap.spcond.del_phy[,1], y = Surr.cmap.spcond.del_phy[,2], type = "l",
     main = "spcond V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.spcond.del_phy[,1], y = Surr.cmap.spcond.del_phy[,3], col = "red")
abline(h = Surr.spcond.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.spcond.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate spcond.chl
plot(x = Surr.cmap.spcond.chl[,1], y = Surr.cmap.spcond.chl[,2], type = "l",
     main = "spcond V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.spcond.chl[,1], y = Surr.cmap.spcond.chl[,3], col = "red")
abline(h = Surr.spcond.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.spcond.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# CMAP INCLUDE DATA
# CMAP 
cmap.spcond.phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.spcond.del_phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.spcond.chl2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# Surrogates
Surr.cmap.spcond.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.spcond.del_phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.spcond.chl2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "spcond", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# LIBMEAN PLOTS
# PHY
cmap.spcond.phy2$LibMeans %>%
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `spcond:phy`, color = "spcond:phy")) +
  geom_line(aes(y = `phy:spcond`, color = "phy:spcond")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$spcond, ag_df_CR$phy)), lty = 2)

# DEL_PHY
cmap.spcond.del_phy2$LibMeans %>%
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `spcond:del_phy`, color = "spcond:del_phy")) +
  geom_line(aes(y = `del_phy:spcond`, color = "del_phy:spcond")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$spcond, ag_df_CR$del_phy)), lty = 2)

# CHL
cmap.spcond.chl2$LibMeans %>%
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `spcond:chl`, color = "spcond:chl")) +
  geom_line(aes(y = `chl:spcond`, color = "chl:spcond")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$spcond, ag_df_CR$chl)), lty = 2)

# Surrogate PHY
Surr.cmap.spcond.phy2$LibMeans %>%
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `spcond:phy`, color = "spcond:phy")) +
  geom_line(aes(y = `phy:spcond`, color = "phy:spcond")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$spcond, ag_df_CR$phy)), lty = 2)

# Surrogate DEL_PHY
Surr.cmap.spcond.del_phy2$LibMeans %>%
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `spcond:del_phy`, color = "spcond:del_phy")) +
  geom_line(aes(y = `del_phy:spcond`, color = "del_phy:spcond")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$spcond, ag_df_CR$del_phy)), lty = 2)

# Surrogate CHL
Surr.cmap.spcond.chl2$LibMeans %>%
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `spcond:chl`, color = "spcond:chl")) +
  geom_line(aes(y = `chl:spcond`, color = "chl:spcond")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$spcond, ag_df_CR$chl)), lty = 2)

# PREDICTSTAT PLOTS
cmap.spcond.phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

cmap.spcond.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

cmap.spcond.chl2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

Surr.cmap.spcond.phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

Surr.cmap.spcond.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

Surr.cmap.spcond.chl2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")
  
  # EMBED DIMENSION
# EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "spcond", target = "phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "spcond", target = "del_phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "spcond", target = "chl", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "spcond", target = "phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "spcond", target = "del_phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "spcond", target = "chl", lib = "1 1174", pred = "1 1174", tau = -7)


```

#DO



```{r}

cmap.do.phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "do", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.do.del_phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "do", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.spcond.chl <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "do", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 


Surr.cmap.do.phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "do", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.do.del_phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "do", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.spcond.chl <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "do", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# CMAP Correlations
do.phy.corr <- cor(cmap.do.phy)
do.phy.corr <- do.phy.corr[1, 3]

do.del_phy.corr <- cor(cmap.do.del_phy)
do.del_phy.corr <- do.del_phy.corr[1, 3]

spcond.chl.corr <- cor(cmap.spcond.chl)
spcond.chl.corr <- spcond.chl.corr[1, 3]

# Surrogate Correlations
Surr.do.phy.corr <- cor(Surr.cmap.do.phy)
Surr.do.phy.corr <- Surr.do.phy.corr[1, 3]

Surr.do.del_phy.corr <- cor(Surr.cmap.do.del_phy)
Surr.do.del_phy.corr <- Surr.do.del_phy.corr[1, 3]

Surr.spcond.chl.corr <- cor(Surr.cmap.spcond.chl)
Surr.spcond.chl.corr <- Surr.spcond.chl.corr[1, 3]

# CMAP PLOTS
# do.phy
plot(x = cmap.do.phy[,1], y = cmap.do.phy[,2], type = "l",
     main = "DO V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.do.phy[,1], y = cmap.do.phy[,3], col = "red")
abline(h = do.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.do.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# do.del_phy
plot(x = cmap.do.del_phy[,1], y = cmap.do.del_phy[,2], type = "l",
     main = "DO V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.do.del_phy[,1], y = cmap.do.del_phy[,3], col = "red")
abline(h = do.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.do.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# spcond.chl
plot(x = cmap.spcond.chl[,1], y = cmap.spcond.chl[,2], type = "l",
     main = "DO V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.spcond.chl[,1], y = cmap.spcond.chl[,3], col = "red")
abline(h = spcond.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.spcond.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate PLOTS
# Surrogate do.phy
plot(x = Surr.cmap.do.phy[,1], y = Surr.cmap.do.phy[,2], type = "l",
     main = "DO V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.do.phy[,1], y = Surr.cmap.do.phy[,3], col = "red")
abline(h = Surr.do.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.do.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate do.del_phy
plot(x = Surr.cmap.do.del_phy[,1], y = Surr.cmap.do.del_phy[,2], type = "l",
     main = "DO V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.do.del_phy[,1], y = Surr.cmap.do.del_phy[,3], col = "red")
abline(h = Surr.do.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.do.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate spcond.chl
plot(x = Surr.cmap.spcond.chl[,1], y = Surr.cmap.spcond.chl[,2], type = "l",
     main = "DO V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.spcond.chl[,1], y = Surr.cmap.spcond.chl[,3], col = "red")
abline(h = Surr.spcond.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.spcond.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# CMAP INCLUDE DATA
# CMAP 
cmap.do.phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "do", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.do.del_phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "do", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.spcond.chl2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "do", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# Surrogates
Surr.cmap.do.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "do", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.do.del_phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "do", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.spcond.chl2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "do", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# LIBMEAN PLOT
# PHY
cmap.do.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`do:phy`,color="do:phy")) +
  geom_line(aes(y=`phy:do`,color="phy:do")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$do,ag_df_CR$phy)),lty=2)
  
# DEL_PHY
cmap.do.del_phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`do:phy`,color="do:del_phy")) +
  geom_line(aes(y=`del_phy:do`,color="del_phy:do")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$do,ag_df_CR$del_phy)),lty=2)
 
# CHL
cmap.spcond.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`do:phy`,color="do:chl")) +
  geom_line(aes(y=`chl:do`,color="chl:do")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$do,ag_df_CR$chl)),lty=2)

# Surrogate PHY
Surr.cmap.do.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`do:phy`,color="do:phy")) +
  geom_line(aes(y=`phy:do`,color="phy:do")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$do,ag_df_CR$phy)),lty=2)
  
# Surrogate DEL_PHY
Surr.cmap.do.del_phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`do:phy`,color="do:del_phy")) +
  geom_line(aes(y=`del_phy:do`,color="del_phy:do")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$do,ag_df_CR$del_phy)),lty=2)
 
# Surrogate CHL
Surr.cmap.spcond.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`do:phy`,color="do:chl")) +
  geom_line(aes(y=`chl:do`,color="chl:do")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$do,ag_df_CR$chl)),lty=2)

# PREDICTSTAT PLOT
cmap.do.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

cmap.do.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize))


+ geom_jitter() + stat_summary(fun = median,geom="line")

cmap.spcond.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# PREDICTSTAT PLOT for Surrogate PHY
Surr.cmap.do.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# PREDICTSTAT PLOT for Surrogate DEL_PHY
Surr.cmap.do.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# PREDICTSTAT PLOT for Surrogate CHL
Surr.cmap.spcond.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# EMBED DIMENSION
# EmbedDimension for PHY
EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "do",
               target = "phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for DEL_PHY
EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "do",
               target = "del_phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for CHL
EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "do",
               target = "chl", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for Surrogate PHY
EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "do",
               target = "phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for Surrogate DEL_PHY
EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "do",
               target = "del_phy", lib = "1 1174", pred = "1 1174",
               tau = -7)

# EmbedDimension for Surrogate CHL
EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "do",
               target = "chl", lib = "1 1174", pred = "1 1174",
               tau = -7)



```


#TURB

```{r}

cmap.turb.phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "turb", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.turb.del_phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "turb", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.turb.chl <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "turb", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.turb.phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "turb", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.turb.del_phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "turb", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.turb.chl <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "turb", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# CMAP
cmap.turb.phy <- CCM(dataFrame = ag_df_CR, E = 5, tau = -7, Tp = 0, columns = "turb", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.turb.del_phy <- CCM(dataFrame = ag_df_CR, E = 5, tau = -7, Tp = 0, columns = "turb", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.turb.chl <- CCM(dataFrame = ag_df_CR, E = 5, tau = -7, Tp = 0, columns = "turb", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# Surrogates
Surr.cmap.turb.phy <- CCM(dataFrame = Surrogate, E = 5, tau = -7, Tp = 0, columns = "turb", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.turb.del_phy <- CCM(dataFrame = Surrogate, E = 5, tau = -7, Tp = 0, columns = "turb", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.turb.chl <- CCM(dataFrame = Surrogate, E = 5, tau = -7, Tp = 0, columns = "turb", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# CMAP CORRELATIONS
turb.phy.corr <- cor(cmap.turb.phy)[1, 3]
turb.del_phy.corr <- cor(cmap.turb.del_phy)[1, 3]
turb.chl.corr <- cor(cmap.turb.chl)[1, 3]

# Surrogate Correlations
Surr.turb.phy.corr <- cor(Surr.cmap.turb.phy)[1, 3]
Surr.turb.del_phy.corr <- cor(Surr.cmap.turb.del_phy)[1, 3]
Surr.turb.chl.corr <- cor(Surr.cmap.turb.chl)[1, 3]

# CMAP PLOTS
# turb.phy
plot(x = cmap.turb.phy[,1], y = cmap.turb.phy[,2], type = "l",
     main = "turb V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.turb.phy[,1], y = cmap.turb.phy[,3], col = "red")
abline(h = turb.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.turb.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# turb.del_phy
plot(x = cmap.turb.del_phy[,1], y = cmap.turb.del_phy[,2], type = "l",
     main = "turb V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.turb.del_phy[,1], y = cmap.turb.del_phy[,3], col = "red")
abline(h = turb.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.turb.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# turb.chl
plot(x = cmap.turb.chl[,1], y = cmap.turb.chl[,2], type = "l",
     main = "turb V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.turb.chl[,1], y = cmap.turb.chl[,3], col = "red")
abline(h = turb.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.turb.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# SURROGATE PLOTS
# Surrogate turb.phy
plot(x = Surr.cmap.turb.phy[,1], y = Surr.cmap.turb.phy[,2], type = "l",
     main = "turb V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.turb.phy[,1], y = Surr.cmap.turb.phy[,3], col = "red")
abline(h = Surr.turb.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.turb.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate turb.del_phy
plot(x = Surr.cmap.turb.del_phy[,1], y = Surr.cmap.turb.del_phy[,2], type = "l",
     main = "turb V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.turb.del_phy[,1], y = Surr.cmap.turb.del_phy[,3], col = "red")
abline(h = Surr.turb.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.turb.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate turb.chl
plot(x = Surr.cmap.turb.chl[,1], y = Surr.cmap.turb.chl[,2], type = "l",
     main = "turb V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.turb.chl[,1], y =Surr.cmap.turb.chl[,3], col = "red")
abline(h = Surr.turb.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.turb.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# CMAP INCLUDE DATA
# CMAP
cmap.turb.phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau = -7, Tp = 0, columns = "turb", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE, includeData = TRUE)

cmap.turb.del_phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau = -7, Tp = 0, columns = "turb", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE, includeData = TRUE)

cmap.turb.chl2 <- CCM(dataFrame = ag_df_CR, E = 5, tau = -7, Tp = 0, columns = "turb", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE, includeData = TRUE)

# Surrogates
Surr.cmap.turb.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau = -7, Tp = 0, columns = "turb", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE, includeData = TRUE)

Surr.cmap.turb.del_phy2 <- CCM(dataFrame = Surrogate, E = 5, tau = -7, Tp = 0, columns = "turb", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE, includeData = TRUE)

Surr.cmap.turb.chl2 <- CCM(dataFrame = Surrogate, E = 5, tau = -7, Tp = 0, columns = "turb", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE, includeData = TRUE)

# LIBMEAN PLOT
# PHY
cmap.turb.phy2$LibMeans %>% 
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `turb:phy`, color = "turb:phy")) +
  geom_line(aes(y = `phy:turb`, color = "phy:turb")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$turb, ag_df_CR$phy)), lty = 2)

# DEL_PHY
cmap.turb.del_phy2$LibMeans %>% 
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `turb:phy`, color = "turb:del_phy")) +
  geom_line(aes(y = `phy:turb`, color = "del_phy:turb")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$turb, ag_df_CR$del_phy)), lty = 2)

# CHL
cmap.turb.chl2$LibMeans %>% 
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `turb:phy`, color = "turb:chl")) +
  geom_line(aes(y = `phy:turb`, color = "chl:turb")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$turb, ag_df_CR$chl)), lty = 2)

# Surrogate PHY
Surr.cmap.turb.phy2$LibMeans %>% 
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `turb:phy`, color = "turb:phy")) +
  geom_line(aes(y = `phy:turb`, color = "phy:turb")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$turb, ag_df_CR$phy)), lty = 2)

# Surrogate DEL_PHY
Surr.cmap.turb.del_phy2$LibMeans %>% 
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `turb:phy`, color = "turb:del_phy")) +
  geom_line(aes(y = `phy:turb`, color = "del_phy:turb")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$turb, ag_df_CR$del_phy)), lty = 2)

# Surrogate CHL
Surr.cmap.turb.chl2$LibMeans %>% 
  ggplot(aes(x = LibSize)) +
  geom_line(aes(y = `turb:phy`, color = "turb:chl")) +
  geom_line(aes(y = `phy:turb`, color = "chl:turb")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$turb, ag_df_CR$chl)), lty = 2)

# PREDICTSTAT PLOT
cmap.turb.phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) + 
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

cmap.turb.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) + 
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

cmap.turb.chl2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) + 
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

# Surrogate PHY
Surr.cmap.turb.phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) + 
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

# Surrogate DEL_PHY
Surr.cmap.turb.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) + 
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

# Surrogate CHL
Surr.cmap.turb.chl2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) + 
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")



# PREDICTSTAT PLOTS
cmap.turb.phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

cmap.turb.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

cmap.turb.chl2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

Surr.cmap.turb.phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

Surr.cmap.turb.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

Surr.cmap.turb.chl2$CCM1_PredictStat %>%
  ggplot(aes(x = LibSize, y = rho, group = LibSize)) +
  geom_jitter() + 
  stat_summary(fun = median, geom = "line")

# EMBED DIMENSION
# Uncomment and replace the placeholder values with appropriate parameters.
# EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "do", target = "phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "do", target = "del_phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "do", target = "chl", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "do", target = "phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "do", target = "del_phy", lib = "1 1174", pred = "1 1174", tau = -7)
# EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "do", target = "chl", lib = "1 1174", pred = "1 1174", tau = -7)


        
        
    

```

#Salinity

```{r}

cmap.Salinity.phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.Salinity.del_phy <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.Salinity.chl <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 


Surr.cmap.Salinity.phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.Salinity.del_phy <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.Salinity.chl <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "chl", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# CMAP Correlations
Salinity.phy.corr <- cor(cmap.Salinity.phy)
Salinity.phy.corr <- Salinity.phy.corr[1, 3]

Salinity.del_phy.corr <- cor(cmap.Salinity.del_phy)
Salinity.del_phy.corr <- Salinity.del_phy.corr[1, 3]

Salinity.chl.corr <- cor(cmap.Salinity.chl)
Salinity.chl.corr <- Salinity.chl.corr[1, 3]

# Surrogate Correlations
Surr.Salinity.phy.corr <- cor(Surr.cmap.Salinity.phy)
Surr.Salinity.phy.corr <- Surr.Salinity.phy.corr[1, 3]

Surr.Salinity.del_phy.corr <- cor(Surr.cmap.Salinity.del_phy)
Surr.Salinity.del_phy.corr <- Surr.Salinity.del_phy.corr[1, 3]

Surr.Salinity.chl.corr <- cor(Surr.cmap.Salinity.chl)
Surr.Salinity.chl.corr <- Surr.Salinity.chl.corr[1, 3]

# CMAP PLOTS
# Salinity.phy
plot(x = cmap.Salinity.phy[,1], y = cmap.Salinity.phy[,2], type = "l",
     main = "Salinity V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.Salinity.phy[,1], y = cmap.Salinity.phy[,3], col = "red")
abline(h = Salinity.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.Salinity.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Salinity.del_phy
plot(x = cmap.Salinity.del_phy[,1], y = cmap.Salinity.del_phy[,2], type = "l",
     main = "Salinity V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.Salinity.del_phy[,1], y = cmap.Salinity.del_phy[,3], col = "red")
abline(h = Salinity.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.Salinity.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Salinity.chl
plot(x = cmap.Salinity.chl[,1], y = cmap.Salinity.chl[,2], type = "l",
     main = "Salinity V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = cmap.Salinity.chl[,1], y = cmap.Salinity.chl[,3], col = "red")
abline(h = Salinity.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.Salinity.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate PLOTS
# Surrogate Salinity.phy
plot(x = Surr.cmap.Salinity.phy[,1], y = Surr.cmap.Salinity.phy[,2], type = "l",
     main = "Salinity V. phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.Salinity.phy[,1], y = Surr.cmap.Salinity.phy[,3], col = "red")
abline(h = Surr.Salinity.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.Salinity.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate Salinity.del_phy
plot(x = Surr.cmap.Salinity.del_phy[,1], y = Surr.cmap.Salinity.del_phy[,2], type = "l",
     main = "Salinity V. del_phy ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.Salinity.del_phy[,1], y = Surr.cmap.Salinity.del_phy[,3], col = "red")
abline(h = Surr.Salinity.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.Salinity.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate Salinity.chl
plot(x = Surr.cmap.Salinity.chl[,1], y = Surr.cmap.Salinity.chl[,2], type = "l",
     main = "Salinity V. chl ", xlab = "LibSize", ylab = "Rho", col = "blue",  ylim = c(0, 1))
lines(x = Surr.cmap.Salinity.chl[,1], y = Surr.cmap.Salinity.chl[,3], col = "red")
abline(h = Surr.Salinity.chl.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.Salinity.chl)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# CMAP INCLUDE DATA
# CMAP 
cmap.Salinity.phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.Salinity.del_phy2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

cmap.Salinity.chl2 <- CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# Surrogates
Surr.cmap.Salinity.phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.Salinity.del_phy2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "del_phy", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

Surr.cmap.Salinity.chl2 <- CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "Salinity", target = "chl", libSizes = "20 200 20", sample = 100, showPlot = TRUE,includeData = TRUE)

# LIBMEAN PLOT
# PHY
cmap.Salinity.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Salinity:phy`,color="Salinity:phy")) +
  geom_line(aes(y=`phy:Salinity`,color="phy:Salinity")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Salinity,ag_df_CR$phy)),lty=2)
  
# DEL_PHY
cmap.Salinity.del_phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Salinity:phy`,color="Salinity:del_phy")) +
  geom_line(aes(y=`del_phy:Salinity`,color="del_phy:Salinity")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Salinity,ag_df_CR$del_phy)),lty=2)
 
# CHL
cmap.Salinity.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Salinity:phy`,color="Salinity:chl")) +
  geom_line(aes(y=`chl:Salinity`,color="chl:Salinity")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Salinity,ag_df_CR$chl)),lty=2)

# Surrogate PHY
Surr.cmap.Salinity.phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Salinity:phy`,color="Salinity:phy")) +
  geom_line(aes(y=`phy:Salinity`,color="phy:Salinity")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Salinity,ag_df_CR$phy)),lty=2)
  
# Surrogate DEL_PHY
Surr.cmap.Salinity.del_phy2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Salinity:phy`,color="Salinity:del_phy")) +
  geom_line(aes(y=`del_phy:Salinity`,color="del_phy:Salinity")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Salinity,ag_df_CR$del_phy)),lty=2)
 
# Surrogate CHL
Surr.cmap.Salinity.chl2$LibMeans %>% 
  ggplot(aes(x=LibSize)) +
  geom_line(aes(y=`Salinity:phy`,color="Salinity:chl")) +
  geom_line(aes(y=`chl:Salinity`,color="chl:Salinity")) +
  geom_hline(aes(yintercept = cor(ag_df_CR$Salinity,ag_df_CR$chl)),lty=2)

# PREDICTSTAT PLOT
cmap.Salinity.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

cmap.Salinity.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

cmap.Salinity.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# Surrogate PREDICTSTAT PLOT
Surr.cmap.Salinity.phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

Surr.cmap.Salinity.del_phy2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

Surr.cmap.Salinity.chl2$CCM1_PredictStat %>%
  ggplot(aes(x=LibSize,y=rho,group=LibSize)) + 
  geom_jitter() + stat_summary(fun = median,geom="line")

# EMBED DIMENSION

# EmbedDimension(dataFrame = ag_df_CR,Tp = 0, columns = "Salinity", target = "phy",lib="1 1174",pred="1 1174",tau=-7)

# EmbedDimension(dataFrame = ag_df_CR,Tp = 0, columns = "Salinity", target = "del_phy",lib="1 1174",pred="1 1174",tau=-7)

# EmbedDimension(dataFrame = ag_df_CR,Tp = 0, columns = "Salinity", target = "chl",lib="1 1174",pred="1 1174",tau=-7)

# EmbedDimension(dataFrame = Surrogate,Tp = 0, columns = "Salinity", target = "phy",lib="1 1174",pred="1 1174",tau=-7)

# EmbedDimension(dataFrame = Surrogate,Tp = 0, columns = "Salinity", target = "del_phy",lib="1 1174",pred="1 1174",tau=-7)

# EmbedDimension(dataFrame = Surrogate,Tp = 0, columns = "Salinity", target = "chl",lib="1 1174",pred="1 1174",tau=-7)






```


#CHL, PHY DEL_PHY

```{r}

cmap.chl.phy <-CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "chl", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.chl.del_phy <-CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "chl", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

cmap.phy.del_phy <-CCM(dataFrame = ag_df_CR, E = 5, tau=-7, Tp = 0, columns = "phy", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.chl.phy <-CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "chl", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr,cmap.chl.del_phy <-CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "chl", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

Surr.cmap.phy.del_phy <-CCM(dataFrame = Surrogate, E = 5, tau=-7, Tp = 0, columns = "phy", target = "del_phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) 

# CMAP Correlations
Celsius.phy.corr <- cor(cmap.Celsius.phy)
Celsius.phy.corr <- Celsius.phy.corr[1, 3]

chl.phy.corr <- cor(cmap.chl.phy)
chl.phy.corr <- chl.phy.corr[1, 3]

chl.del_phy.corr <- cor(cmap.chl.del_phy)
chl.del_phy.corr <- chl.del_phy.corr[1, 3]

phy.del_phy.corr <- cor(cmap.phy.del_phy)
phy.del_phy.corr <- phy.del_phy.corr[1, 3]

# Surrogate Correlations
Surr.chl.phy.corr <- cor(Surr.cmap.chl.phy)
Surr.chl.phy.corr <- Surr.chl.phy.corr[1, 3]

Surr.chl.del_phy.corr <- cor(Surr.cmap.chl.del_phy)
Surr.chl.del_phy.corr <- Surr.chl.del_phy.corr[1, 3]

Surr.phy.del_phy.corr <- cor(Surr.cmap.phy.del_phy)
Surr.phy.del_phy.corr <- Surr.phy.del_phy.corr[1, 3]

# CMAP Plots
# Celsius.phy
plot(x = cmap.Celsius.phy[,1], y = cmap.Celsius.phy[,2], type = "l",
     main = "Celsius V. phy", xlab = "LibSize", ylab = "Rho", col = "blue", ylim = c(0, 1))
lines(x = cmap.Celsius.phy[,1], y = cmap.Celsius.phy[,3], col = "red")
abline(h = Celsius.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.Celsius.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# chl.phy
plot(x = cmap.chl.phy[,1], y = cmap.chl.phy[,2], type = "l",
     main = "chl V. phy", xlab = "LibSize", ylab = "Rho", col = "blue", ylim = c(0, 1))
lines(x = cmap.chl.phy[,1], y = cmap.chl.phy[,3], col = "red")
abline(h = chl.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.chl.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# chl.del_phy
plot(x = cmap.chl.del_phy[,1], y = cmap.chl.del_phy[,2], type = "l",
     main = "chl V. del_phy", xlab = "LibSize", ylab = "Rho", col = "blue", ylim = c(0, 1))
lines(x = cmap.chl.del_phy[,1], y = cmap.chl.del_phy[,3], col = "red")
abline(h = chl.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.chl.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# phy.del_phy
plot(x = cmap.phy.del_phy[,1], y = cmap.phy.del_phy[,2], type = "l",
     main = "phy V. del_phy", xlab = "LibSize", ylab = "Rho", col = "blue", ylim = c(0, 1))
lines(x = cmap.phy.del_phy[,1], y = cmap.phy.del_phy[,3], col = "red")
abline(h = phy.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(cmap.phy.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# Surrogate Plots
# chl.phy
plot(x = Surr.cmap.chl.phy[,1], y = Surr.cmap.chl.phy[,2], type = "l",
     main = "chl V. phy (Surrogate)", xlab = "LibSize", ylab = "Rho", col = "blue", ylim = c(0, 1))
lines(x = Surr.cmap.chl.phy[,1], y = Surr.cmap.chl.phy[,3], col = "red")
abline(h = Surr.chl.phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.chl.phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# chl.del_phy
plot(x = Surr.cmap.chl.del_phy[,1], y = Surr.cmap.chl.del_phy[,2], type = "l",
     main = "chl V. del_phy (Surrogate)", xlab = "LibSize", ylab = "Rho", col = "blue", ylim = c(0, 1))
lines(x = Surr.cmap.chl.del_phy[,1], y = Surr.cmap.chl.del_phy[,3], col = "red")
abline(h = Surr.chl.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.chl.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

# phy.del_phy
plot(x = Surr.cmap.phy.del_phy[,1], y = Surr.cmap.phy.del_phy[,2], type = "l",
     main = "phy V. del_phy (Surrogate)", xlab = "LibSize", ylab = "Rho", col = "blue", ylim = c(0, 1))
lines(x = Surr.cmap.phy.del_phy[,1], y = Surr.cmap.phy.del_phy[,3], col = "red")
abline(h = Surr.phy.del_phy.corr, col = "green", lty = 2)
legend("topright", legend = c(colnames(Surr.cmap.phy.del_phy)[2:3], "Correlation"), 
       col = c("blue", "red", "green"), lty = c(1, 1, 2))

#EMBED DIMENSION 

#EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "Celsius",
               #target = "phy", lib = "1 1174", pred = "1 1174",
               #tau = -7)

#EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "chl",
               #target = "phy", lib = "1 1174", pred = "1 1174",
               #tau = -7)

#EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "chl",
               #target = "del_phy", lib = "1 1174", pred = "1 1174",
               #tau = -7)

#EmbedDimension(dataFrame = ag_df_CR, Tp = 0, columns = "phy",
               #target = "del_phy", lib = "1 1174", pred = "1 1174",
               #tau = -7)

#EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "chl",
               #target = "phy", lib = "1 1174", pred = "1 1174",
               #tau = -7)

#EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "chl",
               #target = "del_phy", lib = "1 1174", pred = "1 1174",
               #tau = -7)

#EmbedDimension(dataFrame = Surrogate, Tp = 0, columns = "phy",
               #target = "del_phy", lib = "1 1174", pred = "1 1174",
               #tau = -7)


```


#CCM MWRA Non-CSO

***CR_bacteria***

#Enteroccus

```{r}

cmap.Enteroccus.del_phy <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "Enteroccus", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.Enteroccus.phy <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "Enteroccus", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.Enteroccus.chl <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "Enteroccus", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


#Surrogates


Surr.cmap.Enteroccus.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Enteroccus", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.Enteroccus.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Enteroccus", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.Enteroccus.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Enteroccus", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)



```

#E_coli

```{r}


cmap.E_coli.del_phy <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "E_coli", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.E_coli.phy <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "E_coli", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.E_coli.chl <- CCM(dataFrame = ag_CR_bacteria, E = 4, Tp = 4, columns = "E_coli", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)




Surr.cmap.E_coli.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "E_coli", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.E_coli.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "E_coli", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.E_coli.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "E_coli", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)



```

***CR_Secchi***

#Total Suspended Solids (mg/L)

```{r}


cmap.TSS.del_phy <- CCM(dataFrame = ag_CR_secchi, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


cmap.TSS.phy <- CCM(dataFrame = ag_CR_secchi, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.TSS.chl <- CCM(dataFrame = ag_CR_secchi, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.TSS.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.TSS.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.TSS.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Total Suspended Solids (mg/L)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

***CR_Nutrients***

#Ammonium (uM)

```{r}


cmap.Ammonium.del_phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


cmap.Ammonium.phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.Ammonium.chl <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.Ammonium.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.Ammonium.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.Ammonium.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Ammonium (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)
```

#"Nitrate+nitrite (uM)"

```{r}


cmap.nitrate_nitrite.del_phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.nitrate_nitrite.phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.nitrate_nitrite.chl <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.nitrate_nitrite.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.nitrate_nitrite.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.nitrate_nitrite.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Nitrate+nitrite (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

#Phosphate (uM)

```{r}


cmap.phosphate.del_phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.phosphate.phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.phosphate.chl <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.phosphate.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.phosphate.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.phosphate.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Phosphate (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

#Total phosphorus (uM)

```{r}


cmap.phosphorus.del_phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.phosphorus.phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.phosphorus.chl <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.phosphorus.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.phosphorus.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.phosphorus.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Total phosphorus (uM)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#Phaeophytin

#Total phosphorus (uM)

```{r}


cmap.Phaeophytin.del_phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phaeophytin (ug/L)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.Phaeophytin.phy <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phaeophytin (ug/L)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.Phaeophytin.chl <- CCM(dataFrame = ag_CR_nutrients, E = 4, Tp = 4, columns = "Phaeophytin (ug/L)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.Phaeophytin.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Phaeophytin (ug/L)", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.Phaeophytin.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Phaeophytin (ug/L)", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.Phaeophytin.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "Phaeophytin (ug/L)", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```


###CCM LOGAN

#HourlyAltimeterSetting

```{r}

cmap.alt.del_phy < - CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyAltimeterSetting", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.alt.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 0, columns = "HourlyAltimeterSetting", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.alt.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 0, columns = "HourlyAltimeterSetting", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.alt.del_phy < - CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyAltimeterSetting", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.alt.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 0, columns = "HourlyAltimeterSetting", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.alt.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 0, columns = "HourlyAltimeterSetting", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)



```

#HourlyDryBulbTemperature

```{r}

cmap.drybulb.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.drybulb.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.drybulb.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.drybulb.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.drybulb.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.drybulb.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyDryBulbTemperature", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyPrecipitation

```{r}

cmap.precip.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.precip.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.precip.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.precip.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.precip.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.precip.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyPrecipitation", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


```

#HourlyRelativeHumidity

```{r}

cmap.humidity.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyRelativeHumidity", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.humidity.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = " HourlyRelativeHumidity", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.humidity.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = " HourlyRelativeHumidity", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.humidity.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyRelativeHumidity", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.humidity.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = " HourlyRelativeHumidity", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.humidity.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = " HourlyRelativeHumidity", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyStationPressure

```{r}

cmap.station.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.station.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.station.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.station.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.station.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.station.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyStationPressure", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyVisibility keep bc effect incident radiation

```{r}

cmap.visibility.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyVisibility", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.visibility.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyVisibility", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.visibility.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyVisibility", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.visibility.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyVisibility", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


Surr.cmap.visibility.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyVisibility", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.visibility.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyVisibility", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)
```

#HourlyWindDirection - could be matter but direction of wind may not
tell how wind is pushing around in charles around. Dan Li. Andy?

```{r}

cmap.wind_direction.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


cmap.wind_direction.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.wind_direction.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.wind_direction.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.wind_direction.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.wind_direction.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindDirection", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

```

#HourlyWindGustSpeed

```{r}

cmap.wind_gust.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.wind_gust.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.wind_gust.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.wind_gust.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.wind_gust.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.wind_gust.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindGustSpeed", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)


#Correlations 

windspeed.phy.corr <- cor(cmap.windspeed.phy)[1, 3]
windspeed.del_phy.corr <- cor(cmap.windspeed.del_phy)[1, 3]
windspeed.chl.corr <- cor(cmap.windspeed.chl)[1, 3]

#Surrogate Correlations

Surr.windspeed.phy.corr <- cor(Surr.cmap.windspeed.phy)[1, 3]
Surr.windspeed.del_phy.corr <- cor(Surr.cmap.windspeed.del_phy)[1, 3]
Surr.windspeed.chl.corr <- cor(Surr.cmap.windspeed.chl)[1, 3]


```

#HourlyWindSpeed - synioptic variable

```{r}

cmap.windspeed.del_phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.windspeed.phy <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

cmap.windspeed.chl <- CCM(dataFrame = ag_Logan, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

#SURROGATE

Surr.cmap.windspeed.del_phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "del_phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.windspeed.phy <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "phy", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

Surr.cmap.windspeed.chl <- CCM(dataFrame = Surrogate, E = 4, Tp = 4, columns = "HourlyWindSpeed", target = "chl", libSizes = "20 200 10", sample = 100, showPlot = TRUE)

#Correlations 

windspeed.phy.corr <- cor(cmap.windspeed.phy)[1, 3]
windspeed.del_phy.corr <- cor(cmap.windspeed.del_phy)[1, 3]
windspeed.chl.corr <- cor(cmap.windspeed.chl)[1, 3]

#Surrogate Correlations

Surr.windspeed.phy.corr <- cor(Surr.cmap.windspeed.phy)[1, 3]
Surr.windspeed.del_phy.corr <- cor(Surr.cmap.windspeed.del_phy)[1, 3]
Surr.windspeed.chl.corr <- cor(Surr.cmap.windspeed.chl)[1, 3]




```
<<<<<<< HEAD
#SURROGATE

```{r}


make_yday_surrogate <- function(yday,ts,bw=28,num_surr=1){
  
  if (any(!is.finite(ts))) {
    stop("SurrogateData(): input time series contained invalid values")
  }
  n = length(ts)
  
  seasonal_cyc = map_dbl(yday,\(yday_i) ksmooth(yday,ts,bandwidth=bw,x.points=yday_i)$y)
  seasonal_resid = ts - seasonal_cyc

#   seasonal_cyc = map_dbl(yday, \(yday_i) ksmooth(as.vector(yday), as.vector(ts), bandwidth=bw, x.points=yday_i)$y)
# seasonal_resid = ts - seasonal_cyc


  # randomize the temporal sequence of residuals and add them back to the cycle.
  
  return(sapply(1:num_surr, function(i) {
    seasonal_cyc + sample(seasonal_resid, n)
  }))
  
  
}

# generate_surrogate <- function(df, var_name) {
#   lapply(1:100, function(i) {
#     data.frame(iteration = i, yday = df$yday, 
#                surr_value = make_yday_surrogate(df$yday, df[[var_name]]))
#   }) %>%
#     do.call(rbind, .) %>%
#     setNames(c("iteration", "yday", paste0(var_name, "_surr")))
# }


do_1_xmap <- function(dataFrame, E, tau, Tp=0, columns, target, lib=NULL, pred=NULL, exclusionRadius, yday_col = "yday") {
  
<<<<<<< HEAD
  
df_phy  <- All.Var %>%
  select(DATE,phy) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_Celsius  <- All.Var %>%
  select(DATE,Celsius) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_spcond  <- All.Var %>%
  select(DATE,spcond) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_do  <- All.Var %>%
  select(DATE,do) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_Salinity  <- All.Var %>%
  select(DATE,Salinity) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_turb  <- All.Var %>%
  select(DATE,turb) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


```


```{r}
df_ph %>%
  ggplot(aes(x=yday,y=ph)) + geom_point(pch=1,alpha=.5)


df_chl %>%
  ggplot(aes(x=yday,y=chl)) + geom_point(pch=1,alpha=.5)


df_Celsius %>%
  ggplot(aes(x=yday,y=Celsius)) + geom_point(pch=1,alpha=.5)

df_spcond %>%
  ggplot(aes(x=yday,y=spcond)) + geom_point(pch=1,alpha=.5)

df_do %>%
  ggplot(aes(x=yday,y=do)) + geom_point(pch=1,alpha=.5)

df_Salinity %>%
  ggplot(aes(x=yday,y=Salinity)) + geom_point(pch=1,alpha=.5)

df_turb %>%
  ggplot(aes(x=yday,y=turb)) + geom_point(pch=1,alpha=.5)


```

```{r}
f_kreg_ph <- ksmooth(df_ph$yday,df_ph$ph,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_chl <- ksmooth(df_chl$yday,df_chl$chl,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_Celsius <- ksmooth(df_Celsius$yday,df_Celsius$Celsius,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_spcond <- ksmooth(df_spcond$yday,df_spcond$spcond,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_do <- ksmooth(df_do$yday,df_do$do,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_Salinity <- ksmooth(df_Salinity$yday,df_Salinity$Salinity,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_turb <- ksmooth(df_turb$yday,df_turb$turb,bandwidth=28,x.points=120:320,kernel="normal") 


```

```{r}
Surrogate_ph <- data.frame(yday=df_ph$yday,ph_surr = make_yday_surrogate(df_ph$yday,df_ph$ph))

Surrogate_chl <- data.frame(yday=df_chl$yday,chl_surr = make_yday_surrogate(df_chl$yday,df_chl$chl))


Surrogate_phy <- data.frame(yday=df_phy$yday,phy_surr = make_yday_surrogate(df_phy$yday,df_phy$phy))


Surrogate_Celsius <- data.frame(yday=df_Celsius$yday,Celsius_surr = make_yday_surrogate(df_Celsius$yday,df_Celsius$Celsius))

Surrogate_spcond <- data.frame(yday=df_spcond$yday,spcond_surr = make_yday_surrogate(df_spcond$yday,df_spcond$spcond))

Surrogate_do <- data.frame(yday=df_do$yday,do_surr = make_yday_surrogate(df_do$yday,df_do$do))

Surrogate_Salinity <- data.frame(yday=df_Salinity$yday,Salinity_surr = make_yday_surrogate(df_Salinity$yday,df_Salinity$Salinity))

Surrogate_turb <- data.frame(yday=df_turb$yday,turb_surr = make_yday_surrogate(df_turb$yday,df_turb$turb))


```

```{r}

#Surrogate_phy <- as.data.frame(Surrogate_phy)
#Surrogate_chl <- as.data.frame(Surrogate_chl)
#Surrogate_ph <- as.data.frame(Surrogate_ph)
#Surrogate_Celsius <- as.data.frame(Surrogate_Celsius)
#Surrogate_spcond <- as.data.frame(Surrogate_spcond)
#Surrogate_do <- as.data.frame(Surrogate_do)
#Surrogate_turb <- as.data.frame(Surrogate_turb)
#Surrogate_Salinity <- as.data.frame(Surrogate_Salinity)
# Surrogate_del_phy <- as.data.frame(Surrogate_del_phy)


Surrogate <- bind_cols(
  Surrogate_phy,
  Surrogate_chl,
  Surrogate_ph,
  Surrogate_Celsius,
  Surrogate_spcond,
  Surrogate_do,
  Surrogate_turb,
  Surrogate_Salinity
 # , Surrogate_del_phy
  
)


Surrogate <- Surrogate[, -c(3, 5, 7, 9, 11, 13, 15)]



# Set the column names
colnames(Surrogate) <- c(
  "yday",
  "phy",
  "chl",
  "ph",
  "Celsius",
  "spcond",
  "do",
  "turb",
  "Salinity"
 # , "del_phy"
)


#Save Surrogate 


# Check if the file exists
if(file.exists("Surrogate")) {
  # Load the file if it exists
  Surrogate <- readRDS("Surrogate.rds")
} else {
  # If the file does not exist, create Multi_E2_D3
  Surrogate <- Surrogate
  # Save Multi_E2_D3 to file
  saveRDS(Surrogate, "Surrogate.rds")
}


```



```{r}

# Assuming df_ph and make_yday_surrogate are already defined

# Generate 100 iterations of the surrogate data
#surrogate_list <- lapply(1:100, function(i) {
  #data.frame(iteration = i, yday = df_ph$yday, 
 #            ph_surr = make_yday_surrogate(df_ph$yday, df_ph$ph))
#})

# Combine all iterations into a single data frame
#Surrogate_ph <- do.call(rbind, surrogate_list)

# View the structure of the resulting data frame
#str(Surrogate_ph)



Surrogate_ph %>%
  ggplot(aes(x=yday,y=ph_surr)) + geom_point(pch=1,alpha=.5)


# Function to generate surrogate data for a given data frame
generate_surrogate <- function(df, var_name) {
  lapply(1:100, function(i) {
    data.frame(iteration = i, yday = df$yday, 
               surr_value = make_yday_surrogate(df$yday, df[[var_name]]))
  }) %>%
    do.call(rbind, .) %>%
    setNames(c("iteration", "yday", paste0(var_name, "_surr")))
}

# Generate surrogate datasets
Surrogate_ph <- generate_surrogate(df_ph, "ph")
Surrogate_chl <- generate_surrogate(df_chl, "chl")
Surrogate_phy <- generate_surrogate(df_phy, "phy")
Surrogate_Celsius <- generate_surrogate(df_Celsius, "Celsius")
Surrogate_spcond <- generate_surrogate(df_spcond, "spcond")
Surrogate_do <- generate_surrogate(df_do, "do")
Surrogate_Salinity <- generate_surrogate(df_Salinity, "Salinity")
Surrogate_turb <- generate_surrogate(df_turb, "turb")

# View structure of one of the datasets
str(Surrogate_ph)

#graphs

Surrogate_ph %>%
  ggplot(aes(x=yday,y=ph_surr)) + geom_point(pch=1,alpha=.5)


Surrogate_chl %>%
  ggplot(aes(x=yday,y=chl_surr)) + geom_point(pch=1,alpha=.5)


Surrogate_phy %>%
  ggplot(aes(x=yday,y=phy_surr)) + geom_point(pch=1,alpha=.5)


Surrogate_Celsius %>%
  ggplot(aes(x=yday,y=Celsius_surr)) + geom_point(pch=1,alpha=.5)

#average together


Surrogate_chl <- Surrogate_chl %>%
  group_by(yday) %>%
  summarise(chl_surr = mean(chl_surr, na.rm = TRUE))

Surrogate_ph <- Surrogate_ph %>%
  group_by(yday) %>%
  summarise(ph_surr = mean(ph_surr, na.rm = TRUE))

Surrogate_phy <- Surrogate_phy %>%
  group_by(yday) %>%
  summarise(phy_surr = mean(phy_surr, na.rm = TRUE))

Surrogate_Celsius <- Surrogate_Celsius %>%
  group_by(yday) %>%
  summarise(Celsius_surr = mean(Celsius_surr, na.rm = TRUE))


Surrogate_spcond <- Surrogate_spcond %>%
  group_by(yday) %>%
  summarise(spcond_surr = mean(spcond_surr, na.rm = TRUE))


Surrogate_do <- Surrogate_do %>%
  group_by(yday) %>%
  summarise(do_surr = mean(do_surr, na.rm = TRUE))


Surrogate_turb <- Surrogate_turb %>%
  group_by(yday) %>%
  summarise(turb_surr = mean(turb_surr, na.rm = TRUE))


Surrogate_Salinity <- Surrogate_Salinity %>%
  group_by(yday) %>%
  summarise(Salinity_surr = mean(Salinity_surr, na.rm = TRUE))

#bind columns


Surrogate <- bind_cols(
  Surrogate_phy,
  Surrogate_chl,
  Surrogate_ph,
  Surrogate_Celsius,
  Surrogate_spcond,
  Surrogate_do,
  Surrogate_turb,
  Surrogate_Salinity
 # , Surrogate_del_phy
  
)


#Surrogate <- Surrogate[, -c(1, 3,5)]
                            
                            
                            
Surrogate <- Surrogate[, -c( 3, 5, 7,9, 11, 13, 15)]



# Set the column names
colnames(Surrogate) <- c(
  "yday",
  "phy",
  "chl",
  "ph",
  "Celsius",
  "spcond",
  "do",
  "turb",
  "Salinity"
 # , "del_phy"
)




```



#CMAP FUNCTION


```{r}

tau_i <- 6




#(1) Run CONVERGENT cross-map for the real time series. Here sample = 100, random = FALSE, and you give a vector of library sizes.


cmap.ph.phy.1 <- CCM(dataFrame = ag_df_CR, E = 6, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "20 40 60 80 100 140 180 240 300 400 500 600 700 800 900 1000 1100 1169", sample = 100, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) #libsize - start 
end space in between


#(2) Run cross-map just at the maximum library size for the "real" time series. Now sample = "1", lib_sizes = "1169", and random = FALSE.


cmap.ph.phy.2 <- CCM(dataFrame = ag_df_CR, E = 6, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "1169", sample = 1, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) #libsize - start end space in between




#(3) Run cross-map just at the maximum library size for each of the 200 SURROGATE time series. Sample = "1", lib_sizes = "1169", random  = FALSE.



cmap.ph.phy.3 <- CCM(dataFrame = Surrogate, E = 6, tau=-7, Tp = 0, columns = "ph", target = "phy", libSizes = "1169", sample = 1, exclusionRadius = tau_i, random = FALSE, showPlot = TRUE) #libsize - start end space in between





#tau is 7
#E of 6 6 EDM back up w/ publication 
#add exclusion radius 
exclusionRadius = tau_i, # exclude 2*tau additional points in cross-val
tau

#real <- lib_sizes = "20 40 60 80 100 140 180 240 300 400 500 600"
#sample <- 100



#lib_sizes = "1169"
#sample = "100"
#random=FALSE



```
#Univar

```{r}

Simplex_tau7_phy

rho_E_tau_i_0 <- EmbedDimension(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                        tau=-tau_i,Tp=tau_i,
lib = lib_ins, pred = lib_ins, showPlot = TRUE, includeData = TRUE) #lib train, #pred is pred 



#SELECT THETA
rho_theta_tau_i <- PredictNonlinear(dataFrame = ag_df_CR, columns = "phy", target = "phy",
                                    E=3,
                                    tau=-tau_i,Tp=tau_i,#exclusionRadius = tau_i,
                                    lib = lib_ins, pred = lib_ins, showPlot = TRUE) #lib train, 
#PREDICT - SMAP

preds_AR <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=3,theta=8) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)

Univar <- data.frame(
  phy = preds_AR$predictions$Predictions,
  date = preds_AR$predictions$date
)

#AR(1)


# we can use S-map with E=1 and theta=0 to get the AR(1) forecast skill
preds_AR <- SMap(dataFrame = ag_df_CR, columns = "phy", target = "phy",
lib = lib_ins, pred = lib_ins, E=1,theta=0,tau=-tau_i,Tp=tau_i,exclusionRadius=tau_i) #lib train, #pred is pred 

stats_AR <- ComputeError(preds_AR$predictions$Observations,
                         preds_AR$predictions$Predictions)

```




