---
title: "Seasonal Surrogates"
author: "E Deyle"
date: "2025-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
```


## R Markdown

We are going to attempt to use `ksmooth()` due to it's syntax set up so that the smoothing parameter is explicitly written as a bandwidth in units of the `x` variable. We are going to use a bandwidth of 28 days, so that the quartiles of the kernal fall into ± 7 days.

```{r cars}
All.Var <- readRDS("~/Research/Water Quality/HAB-Thesis/All.Var.rds")

```

## Propose function

```{r}


make_yday_surrogate <- function(yday,ts,bw=28,num_surr=1){
  
  # ksmooth(df_ph$yday,df_ph$ph,bandwidth=28,x.points=120:320,kernel="normal") 
  
  if (any(!is.finite(ts))) {
    stop("SurrogateData(): input time series contained invalid values")
  }
  n = length(ts)
  
  seasonal_cyc = map_dbl(yday,\(yday_i) ksmooth(yday,ts,bandwidth=bw,x.points=yday_i)$y)
  seasonal_resid = ts - seasonal_cyc
  
  # randomize the temporal sequence of residuals and add them back to the cycle.
  
  return(sapply(1:num_surr, function(i) {
    seasonal_cyc + sample(seasonal_resid, n)
  }))
  
  
}




```

## Examine columns from various data streams

Let's look at turbidity in the Charles River as an example.

```{r pressure, echo=FALSE}


df_ph <- All.Var %>%
  select(DATE,ph) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))

df_chl <- All.Var %>%
  select(DATE,chl) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))
  
  
df_phy  <- All.Var %>%
  select(DATE,phy) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_Celsius  <- All.Var %>%
  select(DATE,Celsius) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_spcond  <- All.Var %>%
  select(DATE,spcond) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_do  <- All.Var %>%
  select(DATE,do) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_Salinity  <- All.Var %>%
  select(DATE,Salinity) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


df_turb  <- All.Var %>%
  select(DATE,turb) %>%
  mutate(yday = yday(DATE)) %>%
  filter(complete.cases(.))


```

```{r}
df_ph %>%
  ggplot(aes(x=yday,y=ph)) + geom_point(pch=1,alpha=.5)


df_chl %>%
  ggplot(aes(x=yday,y=chl)) + geom_point(pch=1,alpha=.5)


df_Celsius %>%
  ggplot(aes(x=yday,y=Celsius)) + geom_point(pch=1,alpha=.5)

df_spcond %>%
  ggplot(aes(x=yday,y=spcond)) + geom_point(pch=1,alpha=.5)

df_do %>%
  ggplot(aes(x=yday,y=do)) + geom_point(pch=1,alpha=.5)

df_Salinity %>%
  ggplot(aes(x=yday,y=Salinity)) + geom_point(pch=1,alpha=.5)

df_turb %>%
  ggplot(aes(x=yday,y=turb)) + geom_point(pch=1,alpha=.5)


```

```{r}
f_kreg_ph <- ksmooth(df_ph$yday,df_ph$ph,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_chl <- ksmooth(df_chl$yday,df_chl$chl,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_Celsius <- ksmooth(df_Celsius$yday,df_Celsius$Celsius,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_spcond <- ksmooth(df_spcond$yday,df_spcond$spcond,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_do <- ksmooth(df_do$yday,df_do$do,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_Salinity <- ksmooth(df_Salinity$yday,df_Salinity$Salinity,bandwidth=28,x.points=120:320,kernel="normal") 

f_kreg_turb <- ksmooth(df_turb$yday,df_turb$turb,bandwidth=28,x.points=120:320,kernel="normal") 


```


```{r}
Surrogate_ph <- data.frame(yday=df_ph$yday,ph_surr = make_yday_surrogate(df_ph$yday,df_ph$ph))

Surrogate_chl <- data.frame(yday=df_chl$yday,chl_surr = make_yday_surrogate(df_chl$yday,df_chl$chl))


Surrogate_phy <- data.frame(yday=df_phy$yday,phy_surr = make_yday_surrogate(df_phy$yday,df_phy$phy))


Surrogate_Celsius <- data.frame(yday=df_Celsius$yday,Celsius_surr = make_yday_surrogate(df_Celsius$yday,df_Celsius$Celsius))

Surrogate_spcond <- data.frame(yday=df_spcond$yday,spcond_surr = make_yday_surrogate(df_spcond$yday,df_spcond$spcond))

Surrogate_do <- data.frame(yday=df_do$yday,do_surr = make_yday_surrogate(df_do$yday,df_do$do))

Surrogate_Salinity <- data.frame(yday=df_Salinity$yday,Salinity_surr = make_yday_surrogate(df_Salinity$yday,df_Salinity$Salinity))

Surrogate_turb <- data.frame(yday=df_turb$yday,turb_surr = make_yday_surrogate(df_turb$yday,df_turb$turb))


```


```{r}

Surrogate_phy <- as.data.frame(Surrogate_phy)
Surrogate_chl <- as.data.frame(Surrogate_chl)
Surrogate_ph <- as.data.frame(Surrogate_ph)
Surrogate_Celsius <- as.data.frame(Surrogate_Celsius)
Surrogate_spcond <- as.data.frame(Surrogate_spcond)
Surrogate_do <- as.data.frame(Surrogate_do)
Surrogate_turb <- as.data.frame(Surrogate_turb)
Surrogate_Salinity <- as.data.frame(Surrogate_Salinity)
Surrogate_del_phy <- as.data.frame(Surrogate_del_phy)


Surrogate <- bind_cols(
  Surrogate_phy,
  Surrogate_chl,
  Surrogate_ph,
  Surrogate_Celsius,
  Surrogate_spcond,
  Surrogate_do,
  Surrogate_turb,
  Surrogate_Salinity,
  Surrogate_del_phy
  
)


# Set the column names
colnames(Surrogate) <- c(
  "phy",
  "chl",
  "ph",
  "Celsius",
  "spcond",
  "do",
  "turb",
  "Salinity",
  "del_phy"
)
```

