
---
title: "03_multivariate_EDM"
output: html_document
date: "2024-04-03"
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---



### Muiltivariate S-Map

-   rho_theta_e3

    -   Theta

    -   Rho

```{r}

rho_theta_e3 = PredictNonlinear(dataFrame = ag_df_CR, columns = "chl",
target = "chl", lib = lib_ins, pred = lib_ins, E = 4)

```

### **Evaluate Simplex Prediction** - out of sample forecasting (figure 5) 

-   ag_df_CRPredict

    -   Observations

    -   Predictions

    -   Pred_Variance

```{r}

ag_df_CRPredict <- Simplex(dataFrame = ag_df_CR,lib = lib_ins, pred = lib_ins, pred = "1076 1223", target = "chl",
columns = "chl", E = 4)

#S-Map = Theta



```

```{r}

 ComputeError(ag_df_CRPredict$Observations, ag_df_CRPredict$Predictions)
 
```

### Evaluate S-Map - Multivar 

It can be advantageous to combine different time series to create the
phase-space embedding, providing they are observed from the same system.

-   Smap

    -   predictions

    -   coefficents

    -   singularvalues

    -   ∂chl/∂chl(t-1,2,3,4)

**#Where does TentMapNoise come from? SMapPredict?**

**Tentmap Noise = Theta?**

**What is columns?**

```{r}

 #If θ= 0, all library points have the same weight regardless of the local state of the predictee; 

smap = SMap(dataFrame = ag_df_CR, lib = lib_ins, pred = lib_ins, target = "chl",
columns = "chl", E = 4, theta = 5)

#if h > θ, the forecast given by the S-map depends on the local state of the predictee, and thus produces locally different fittings.
#smap = SMap(dataFrame = ag_df_CR, lib = "1 1075", pred = "1076 1223", target = "chl",
#columns = "chl", E = 2, theta = 0)

```

```{r}
head(cbind(smap$predictions, smap$coefficients), 2)

tail(cbind(smap$predictions, smap$coefficients))


```

# EDM Mulit-variate Analysis


Next Steps

Convergent Cross Mapping All possible Covariates in one data frame as
different columns other variables all the endogenous bigoeochemical and
human drivers management driver and - rainfall and CSOs know now half
week to weekly time scale we see has signature until we have the
corrected values to keep the diff 9 to noon 4 days negative auto, use
linear s-map To make forecasts: predict 1st differences and add back
into data prediction for tomorrow is value for tomorrow + value for
today

list of measurments and list of weekly measurments look at Tahoe +
geneva

plot minutes vs. volume CSOs - rainfall causal associations? analysis:
same trend = synchornity not = one is low and flat is oneway causal\
number at end matters, consider as correlation coeff, rho ccm at max
library size

look at full matrix with nutrient time series later on

2 different data matrixes 1. time-scale 2. timespan

#EDM MULTIVARIATE

#MULTIVIEW

ccm uses y to predict x, if true, x can affect y ccm wraps (Simplex
target = x, columns = y)

multivariate Simplex ( Embedded = True, columns = c("x1, "x2)) set CCM
samples to 10 to see result


#Multiview

Here, we demonstrate this idea using the Multiview() function with the
3-species data used above. Multiview() operates by constructing all
possible embeddings of dimension E with lag up to E-1. These embeddings
are ranked by forecast skill (rho) over the lib portion of the data. The
individual forecasts for the top multiview embeddings are then averaged
together. If multiview is not specified it is set to sqrt(C) where C is
the number of E-dimensional combinations created from all data vectors.

View lists the various combinations of data embedding vectors used for
the forecasts along with their prediction statistics. Predictions
returns the final averaged multiview projections.

E is amounts of lags. univar time lags D is dimension of individual
multivariate models, number of vars we're taking at a time. axis to
embed. Additional Analysis fills in mechnaistically. Can set lib = pred
At least E of 2, after E \> 5 com sci problem

```{r}
Multiview2 = Multiview(dataFrame = ag_df_CR, lib = "1 1048", pred = "1 1048", E = 3, D= 5,
                       
  columns = c("chl", "ph", "Celsius", "spcond", "do", "turb", "Salinity"), 
  target = "phy")
Multiview2()


**DIFFERENCE BETWEEN Multiview 2 and Multiview**?

```

\#**TEST**

# Check if the file exists

#if(file.exists("Multi_E2_D3.rds")) { \# Load the file if it exists
Multi_E2_D3 \<- readRDS("Multi_E2_D3.rds") #} else { \# If the file does
not exist, create Multi_E2_D3 Multi_E2_D3 \<- Multiview(dataFrame =
ag_df_CR, \# lib = "1 1014", pred = "1 1014", \# in-sample \# lib = "1
1014", pred = "1015 1189", \# out-sample \# trainLib = TRUE, \# E = 2,
D=3, \# tau = -7, Tp = 7, \# columns = "chl phy ph Celsius spcond do
turb Salinity", #target = "phy") \# Save Multi_E2_D3 to file \#
saveRDS(Multi_E2_D3, "Multi_E2_D3.rds") #}

```{r}


#Mutltiview

#Omit NAs 

ag_df_CR <- na.omit(ag_df_CR)


# Find the first row number for the first date in 2023
first_row_2023 <- which(format(ag_df_CR$date, "%Y") == "2023")[1]

print(first_row_2023)

#Check class

ag_df_CR$date <- as.numeric(ag_df_CR$date)
library(rEDM)


#**E3 D5 IN SAMPLE**

# Check if the file exists
if(file.exists("Multi_E3_D5.rds")) {
  # Load the file if it exists
  Multi_E3_D5 <- readRDS("Mutliview_E3D5.rds")
} else {
  # If the file does not exist, create Multi_E2_D3
  Multi_E3_D5 <- Multiview(dataFrame = ag_df_CR, lib = "1 1014", pred = "1 1014", E =3, D=5,
                            columns = "chl phy ph Celsius spcond do turb Salinity sin_season", target = "phy")
  # Save Multi_E2_D3 to file
  saveRDS(Multi_E3_D5, "Mutliview_E2D5.rds")
}



#**E2 D3 IN SAMPLE**

Multi_E2_D3 <- "Multi_E2_D3.rds"
if(!file.exists("Multi_E2_D3.rds")){
 Multi_E2_D3 <- Multiview(dataFrame = ag_df_CR, lib = "1 1014", pred = "1 1014", E = 2, D=3,
                            columns = "chl phy ph Celsius spcond do turb Salinity sin_season", target = "phy")
    save(Multi_E2_D3, file = "Multi_E2_D3.rds")
} else{
  load(Multi_E2_D3)
}


#HEAD


head(Multi_E2_D3)
  
head(Multi_E3_D5)
  
  

```